### 2021-08-16 paper/main.tex
update the tex file for IEEE style

\documentclass[conference]{IEEEtran}
\usepackage[utf8]{inputenc}

\title{COMPX527 Assignment 1 Report}

\author{
\IEEEauthorblockN{Glenn Cumming}
\IEEEauthorblockA{Department of Computer Science\\
  \textit{University of Waikato}\\
  Hamilton, New Zealand\\
  \texttt{glenn@hif.nz}}
  \and
\IEEEauthorblockN{Mitchell Grout}
\IEEEauthorblockA{Department of Computer Science\\
  \textit{University of Waikato}\\
  Hamilton, New Zealand\\
  \texttt{mjg44@students.waikato.ac.nz}}
  \and
\IEEEauthorblockN{Shufen Li}
\IEEEauthorblockA{Department of Computer Science\\
  \textit{University of Waikato}\\
  Hamilton, New Zealand\\
  \texttt{sl302@students.waikato.ac.nz}}
  \and
\IEEEauthorblockN{Sunny Chikara}
\IEEEauthorblockA{Department of Computer Science\\
  \textit{University of Waikato}\\
  Hamilton, New Zealand\\
  \texttt{sc420@students.waikato.ac.nz}}
  \and
\IEEEauthorblockN{YingJun Huang}
\IEEEauthorblockA{Department of Computer Science\\
  \textit{University of Waikato}\\
  Hamilton, New Zealand\\
  \texttt{yh320@students.waikato.ac.nz}}
}
\begin{document}

\maketitle

\begin{abstract}
We designed an Object Detection web service on the AWS Cloud Provider, using Terraform for programmable infrastrucure, Ansible for deployment, and Python for the web service and object detection.
\end{abstract}
\begin{IEEEkeywords}
AWS, COMPX527, Terraform, Ansible, Flask, Python, Object Detection, Retinanet
\end{IEEEkeywords}
\section{Solution Summary}
The Flask Object Detection service is a load balanced HTTP service deployed in AWS EC2, using the AWS ELB load balancer. The service can accept a JPG image and run object detection on it, and returns the resulting image with identified objects highlighted.
\section{Motivation}
We decided on object detection in the cloud in order to learn and appricate the challenges of providing a stateless, scalbale service that could be used for a variey of other projects. Examples included
\begin{itemize}
\item Contexutal threat analysis, such as humans detected in an area which should only include livestock.
\item Numbercial anyalisis, such as the number of a species of wildlife in an area over time.
\item Absence detection, indetifying objects that should be in an image but are not
\end{itemize}
\section{Proposed Solution}
An Amazon Web Services based cluster of web servers taking images from clients and returning images with bionding boxed indetified objects plus json formatted data, behind an Eleastic Load Balancer. The cluster will be horizontally scalable by adding web servers, and accessable via curl or any other HTTP client that can perform HTTP POST requests. It was trained used the AWS COCO data set \footnote{https://registry.opendata.aws/fast-ai-coco/}, and also used the set to for testing and demonstrations. 
\section{Solution Architecture}
We decided to use a load balanced web service architecture, a very common and well understood model with common solutions to scalability and uptime. We have the following components and features:
\subsection{The Image Processing Server}
The project uses the Retinanet based Object Detection developed by Keras
\footnote{https://github.com/fizyr/keras-retinanet}. The web service was developed in Python using a Flask server \footnote{https://pypi.org/project/Flask/}.\par
The server recives via HTTP JPG formatted image, and returns the image with bounding boxes around identified objects, plus JSON data of the images.
\subsection{The Load Balancer}
The object detection being inhernetly slow forces the use of laod balancing and scaling techniques. Using the AWS Elastic Load Balancer allowed us balance the HTTP requests over two or more EC2 servers running the Flask servers. We could create as many Flask servers as we wished, although of course this lent itself to waisted compute resources. Though we had great sucess early on using AWS AutoScaling Groups, which allows a lower and upper limit of EC2 instances running our Flask server to be defined, this functionality was not avalible in the student accounts.
\subsection{The Web User Interface}
In order to have a better demo, it was decided to go ahead and produce a web site interface that would allow uploading 
\subsection{The Web API}
The intended standard way to interact with the Flask Object Detection Cluster is to access it via HTTP calls using the url http://\textless load\_balancer\_fqdn\textgreater/detect. As the system is inteneded for the use of non-private images no ssl was implemented on the load balancer, though it is supported.
\subsection{Amazon Web Services Cloud}
The service running on the Amazon Web Services Cloud, the required choice of the assignment. Though later in lectures there it wa smentioned we could look in to using other Cloud Service Providers, we decied we had already made enough progress to commit ourselves to AWS for this project. Though we did use terraform, which supports IaaS deployments with mulitple CSP, in case we had a need to effect a change quickly.

\section{Technology}
The following are the significant technologies we used in this assignment.
\subsection{Retinanet}
Retinanet is an open source object detection neural net. This technology was chosen for the following reasons \footnote{}.
\begin{itemize}
\item Free Open Source project obviously beneficial for a project with a limited budget.
\item Python 3 for rapid development and deploymewnt. With a mix of experinced and less experinced team members this was particulary useful.
\item Specific instructions using it with the dataset avaliable on the Registry of Open Data on AWS \footnote{https://registry.opendata.aws/fast-ai-coco/}
\end{itemize}
\subsection{Terraform}
Terraform was given in as an example of the provisioning service to use in this assignment. AWS CloudFormation was another option suggested. The decision to go with terraform rather than CloudFormation was based on the following
\begin{itemize}
  \item CloudFormation is prioritory and is specific to AWS cloud offierings. Though this assigmnet is on a small and temporty scale, we still not want to use a technology that would create vendor lockin
  \item Terraform supports provisioning many different platforms, both open standards and priopritary, such as Azure, Goolge Cloud, Kubernetes and OpenStack \footnote{https://aws.amazon.com/cloudformation/}. Developng expericne in deployments with terraform therefore was demied to be more useful.
\end{itemize}
\subsection{Ansible}
Though Terraform is capable of running commands post-install in order to install services and other software needed for our cluster, our cluster used Ansible playbooks instead. Though it meant learning another technology, we demeed a good use of our time since:
\begin{itemize}
  \item Terraform can only run scripts, which would have to be created.
  \item Ansible's langauge is very flxible and is created specifally for the purpose of delpoymnet.
  \item This is a recommended approach by HashiCorp, the devlopers of Terraform. \footnote{https://www.hashicorp.com/resources/ansible-terraform-better-together}
\end{itemize}

\subsection{Github}
We used github for source control of all documents and code. This was chosen over other solutions suc h as SVN and Mecurial due to the familiarity of some of the team members with git. Others in our team have leanrt cloning, pulling and branching. \footnote{https://github.com/}
\subsection{Slack}
As we needed to communicate effectively over a period of weeks without seeing each other often, we decided to use the colloberation software Slack \footnote{https://slack.com/}. We used a free account, and created a channel to allow us to privately communicate about our work. It was used extensively and allowed constant effecteive communication.
\subsection{Trello}
In ordr to break up and manage tasks we created a Kanban Board in Trello \footnote{https://trello.com/}. This got us started with basic learning and setup tasks early on, but as the project progressed we tended to move to the use of Slack to define and assign tasks and workloads.
\subsection{LaTex}
LaTex \footnote{https://www.latex-project.org/} is the accepted standard for scientific papers; therefore although the assignment pointed us to the IEEE A4 standard for reporting, we opted to use the LaTex standard. This gave us very useful experince in using LaTex for proper report formatting.
This report was created in LaTex using the IEEEtran document class provided by IEEE template avaliable at
\footnote{https://www.ieee.org/conferences/publishing/templates.html}
, and generated into PDF by Gnome LaTeX
\footnote{https://wiki.gnome.org/Apps/GNOME-LaTeX}
\subsection{Flask}
The decision to develop and depoly a service using the keras-retinanet Python library immediately suggested to us we should again use Python to provide the web service. Our team had develpoers with experince in both Tornado and Flask; Flask was used as the web service development fell on the person with Flask experince. Both solutions would have been suitable.
\section{Existing object detection soltutions}
There is a wide range of cloud and non cloud solutions. A comparison of these to our own solution is beyound the scope of this document. Those provided by the large Cloud Service Providers includes:
\subsection{Rekognition}
Amazon's object detection solution \footnote{https://aws.amazon.com/rekognition/}.
\subsection{Vision AI}
Google's object detection solution \footnote{https://cloud.google.com/vision/}.
\subsection{Computer Vision}
Microsofts object detection solution \footnote{https://azure.microsoft.com/en-us/services/\\cognitive-services/computer-vision/}.

\section{Security and Vunlerability Assessment}
\subsection{Data Security}
The Flask Object Detection Cluster was specifically created to be stateless and public. Interception of HTTP requests and results can be easily interceptied by third parties with access to the networks between the client and the service. Users of the service should be aware that any images sent or data recived from the service could be illictly obtained, mallicously modified, or corrupted in transit. \par
Migtigation could be acheived by adding SSL encryption and offloading it at the load balancer.
\subsection{Access Security}
\paragraph{Identity and Access Management}
Management access of the resources residing on AWS is protected via the AWS Identity and Access Management (IAM) system \footnote{https://docs.aws.amazon.com/IAM/latest/UserGuide/introduction.html}. We used individual accounts provided by the course. If an account was compromised the it would allow malicous actors to shut down services, or replace the current services with malacoius alternatives. For example, they cloud replace an instance with one that will return malware embeded in an image. \par
Mitigation can be using good protection practices for authentication information, Two Factor Auth (2FA), regular monitoring of the service with a set of well known HTTP requests checked against expected results.
\paragraph{Server Access}
The Flask servers are publically accessable via SSH, needed for deployment. If the key pair is compromised or the keys obtained then root access to the Flask servers cloud be obtained. This would grant the attacker full acccess and the ability to use the server's resources for there own purposes. \par
Migragtion can be using ssh key passwords, encrypted storage of the keys, checking server hashes, and keeping ssh software up to date with security patches.
\subsection{Network Security}
We used AWS Security Groups to restrict the Load Balancer to only ingress traffic port 80. The Image Processers restricted to port 22 and 80. \par
Allowing direct access to the service port is a known problem that could allow an attaacker to easily DDOS a single server, bypassing the Load Balancer. To mitigate this we need to work out how to define the CIDR range in the security group to match the internal IP of the Load Balancer.
The service is load banced, but we where not able to use AutoScaling Groups due to our account restrictions. This results in having to manually create additional servers to cope with increased requests, and so a DDOS would be more effective since a human will have to respond to any such attack.\par
To mitigate this we should move to an account that allows the use of Auto Scaling Groups.  
\subsection{Monitoring and Security}
AWS EC2 instance monitoring was enabled during the terraform creation of the cluster. ELB monitors the avalibility of the Flask HTTP servers. The lack of external monitoring means that we are totally dependent on AWS for security checks and uptime monitoring. \par
Mitigation of the lack of monitoring is obviousloy acheived by using both in house and monitoring services. Common examples of in house monioring is via Nagios, Icinga2, Munin and Promethues. Monitoring services include Uptime.com \footnote{https://uptime.com/uptime-monitoring} for ping and HTTP monitoring, and Paessler \footnote{https://www.paessler.com/port\_monitoring}, which provides addiotnal services such as port monitoring.

\section{Actual AWS Expenditure}
TODO
\section{Future Improvements}
\paragraph{Packaging}
Deployment scripts were chosen for deployment and running the services. However, if the service was to be developed further we would being to use stdeb \footnote{https://pypi.org/project/stdeb/} for packaging for the Ubuntu servers, and potentially set up a Personal Package Archive \footnote{https://help.ubuntu.com/community/PPA}. This would ensure futher development and upgrades by making it part of the standard apt package management system.
\paragraph{Service Management}
Currently the starting and stopping of the service is done via control scripts. These would be integrated in to systemd service management \footnote{https://wiki.debian.org/systemd}.
\paragraph{HTTP}
The service is stateless, plublic and insecure. If a layer of security is desired to protect the data in transit, then HTTPS can be added to the Elastic Load Balancer via the AWS Certificate Manager \footnote{https://docs.aws.amazon.com/elasticloadbalancing\\/latest/classic/ssl-server-cert.html}. The simple reason for not using this was cost: we would have to pay for extra services when our budget was tight.
\paragraph{Cloudflare Multi Region Load Balancing}
Redeployment of the service changes the FQDN in the URL. Also, the service is currenlty deployed on only one region. The Cloudflare Load Balancing would allow the use of many regions or in fact many Cloud Providers to be used with a single contant url presented to the send consumer. The fact that the service is stateless makes it very suitable to this form of scale out \footnote{https://www.cloudflare.com/load-balancing/}
\paragraph{Monitoring}
Future development of the cluster would likely use additional monitoring of performance, costs and uptimes using dedicated EC2 instances, and such existing monitoring systems as Icinga2, Promethues and Munin. Uptime moniroing would of nessescity be run etxernally, such as on internal machines or another cloud providers offering. \par
We would also start to use third party external monitoring services such as Uptime.com \footnote{https://uptime.com/uptime-monitoring} or Paessler \footnote{https://www.paessler.com/}
\section{Team Members Contributions}
\section{Assignment Requirements Completion}
The requirements for this Assignment were communicated in serveral ways, including the assignment documentation, messages in the Moodle channel, the lectures, and by asking the lectuerer and asistant directly. We treated these as customer reuirements, which typically start with a good understanding of the desired outcomes and often require feedback from the customer to ensure we are achiving them.\par
The following is what we have determine dto be the requirements, and how we have achived each one.
\begin{itemize}
  \item Use of AWS to create a non-trivial service, demonstrating our understanding of cloud technologies, their use, and their challenges.
  \item Use of technologies such as Terraform, Ansible and Cloud Formation for programmably defined infrastructure and depoyments
  \item Use of a open dataset from AWS
  \item Work within a team with very diverse technical backgrounds and manage them to ensure fair distribution of the work.
\end{itemize}
.
\end{document}

### 2021-08-17 Test.java
Tom创建分支TO

@@ -1,0 +1,1 @@
+userName:Tom

### 2021-08-17 hello.java
删除

@@ -1,5 +1,0 @@
-public class hello{
-    public static  void main(String[] args){
-        System.out.println("进行测试合并");
-    }
-}

### 2021-08-17 test.java

@@ -1,1 +1,0 @@
-username:Simon

### 2021-08-18 Java/src/main/java/com/hy/compx5270817/RenProApplication.java
更改打包方式(War)

@@ -1,0 +1,34 @@
+package com.hy.compx5270817;
+
+import org.springframework.boot.SpringApplication;
+import org.springframework.boot.autoconfigure.SpringBootApplication;
+import org.springframework.boot.builder.SpringApplicationBuilder;
+import org.springframework.boot.web.servlet.support.SpringBootServletInitializer;
+import org.springframework.context.annotation.Bean;
+import org.springframework.web.servlet.LocaleResolver;
+import org.springframework.web.servlet.i18n.CookieLocaleResolver;
+
+import javax.swing.*;
+import java.util.Locale;
+
+@SpringBootApplication
+public class RenProApplication extends SpringBootServletInitializer {
+
+    @Override
+    protected SpringApplicationBuilder configure(SpringApplicationBuilder application){
+        return application.sources(RenProApplication.class);
+    }
+
+    public static void main(String[] args){
+        SpringApplication.run(RenProApplication.class,args);
+    }
+
+    @Bean
+    public LocaleResolver localeResolver(){
+        CookieLocaleResolver slr = new CookieLocaleResolver();
+        slr.setDefaultLocale(Locale.CHINA);
+        //设置cookie有效期
+        slr.setCookieMaxAge(3600);
+        return slr;
+    }
+}

### 2021-09-01 data/processor/crawler.py
data processor native support

@@ -3,6 +3,7 @@ import json
 import boto3
 from urllib.request import urlopen
 from file_utils import FileUtils
+from sns_processor import process
 
 SQS_CLIENT = boto3.client('sqs') 
 
@@ -10,6 +11,8 @@ global url
 url = 'https://globalnightlight.s3.amazonaws.com/VIIRS_npp_catalog.json'
 
 wait_area = FileUtils.WAIT_LIST
+
+native_run = FileUtils.native_run
 
 def url_to_json(url: str):
     with urlopen(url) as furl:
@@ -30,28 +33,34 @@ def get_links(catalog: json, url: str):
             items.append(base_url + ((link['href']).replace('./','')))
     return children, items
 
- 
+
 
 # STAC processing...  sqs: child-link and push item into sns
 def native_handle_sqs(event, context):
     global counter
     records = event['Records']
-    to_be_visited_queue = os.environ['CATALOG_CRAWL_QUEUE']
-    item_topic_arn = os.environ['STAC_ITEM_TOPIC']
-    max_link = int(os.environ['MAX_CHILDREN'])
-    max_item = int(os.environ['MAX_ITEM'])
+    if native_run == False:
+        to_be_visited_queue = os.environ['CATALOG_CRAWL_QUEUE']
+        item_topic_arn = os.environ['STAC_ITEM_TOPIC']
+        max_link = int(os.environ['MAX_CHILDREN'])
+        max_item = int(os.environ['MAX_ITEM'])
 
     for record in records:    
         url = record['body']
-       
+        print('[INFO] process filename:{}'.format(url))
         catalog = url_to_json(url)
         child_links, items = get_links(catalog, url)
-        for index, clink in enumerate(child_links):
-            SQS_CLIENT.send_message(QueueUrl=to_be_visited_queue,
-                                        MessageBody=clink)
-            print('Catalog inserted: ', clink)
-            #native_handle_sqs(clink)  # can be pushed to SQS
-
+        for clink in child_links:
+            print('[INFO] Catalog inserted: ', clink)
+            if native_run == False:
+                SQS_CLIENT.send_message(QueueUrl=to_be_visited_queue, MessageBody=clink)
+            else:
+                exx = {'Records':[
+                            {'body':clink},   
+                    ]}
+                native_handle_sqs(exx, None)
+            print('[INFO] Catalog inserted OK: ', clink)
+        print('[INFO] clink size:{} items size:{}'.format(str(len(child_links)), str(len(items))))
         for item in items:
             itr = url_to_json(item)
[…]

### 2021-09-01 data/processor/file_utils.py

@@ -36,10 +36,11 @@ class FileUtils:
     Provides utility IO file functions.
     """
     ChinaArea = [108.990515,20.319485,130.478558,40.992357]
-    NZArea = [163.888049,-31.69433,-171.825824,-52.621956]
-    MiddleEastArea = [35.991737,39.298213,72.78633,24.828731]
+    NZArea = [180,-52.621956, 163.888049,-31.69433]
+    MiddleEastArea = [35.991737,24.828731,72.78633,39.298213]
     
     WAIT_LIST = {0:ChinaArea, 1:NZArea, 2:MiddleEastArea}
+    native_run = True
 
     def exsit_native_path(file_path):
       return os.path.exists(file_path)
@@ -74,12 +75,11 @@ class FileUtils:
             
         return False
 
+
+
     def is_overlap(bbox1, bbox2):
-        x1 = max(bbox1[0],bbox2[0]) #108
-        y1 = max(bbox1[1],bbox2[1]) #130 
-        x2 = min(bbox1[2],bbox2[2]) #119
-        y2 = min(bbox1[3],bbox2[3]) #40
-        if x1 < x2 and y1 < y2:
-            return True
-        else:
-            return False
+        isOverlapping = FileUtils.is_overlap_line(bbox1[0],bbox1[2],bbox2[0],bbox2[2]) and FileUtils.is_overlap_line(bbox1[1],bbox1[3],bbox2[1],bbox2[3]) 
+        return isOverlapping
+
+    def is_overlap_line(min1, max1, min2, max2):
+        return min(max1, max2) - max(min1, min2) > 0

### 2021-09-01 data/processor/sns_processor.py

@@ -11,6 +11,7 @@ from sm_mysql import Sec_Mysql
 import datetime 
 
 wait_area = FileUtils.WAIT_LIST
+native_run = FileUtils.native_run
 
 s3 = boto3.client('s3')
 

### 2021-09-01 Java/src/main/java/com/light/Test.java
rds db support

@@ -1,6 +1,6 @@
 package com.light;
 
-import com.light.Util.HttpsUtil;
+import com.light.util.HttpsUtil;
 
 public class Test {
     public static void main(String[] args) throws Exception {

### 2021-09-01 Java/src/main/java/com/light/Util/AnyTrustStrategy.java

@@ -1,4 +1,4 @@
-package com.light.Util;
+package com.light.util;
 
 import org.apache.http.ssl.TrustStrategy;
 

### 2021-09-01 Java/src/main/java/com/light/Util/HttpsUtil.java

@@ -1,4 +1,4 @@
-package com.light.Util;
+package com.light.util;
 
 import java.io.IOException;
 import java.io.InputStream;

### 2021-09-01 Java/src/main/java/com/light/controllers/GithubLogController.java

@@ -2,8 +2,8 @@ package com.light.controllers;
 
 
 import com.alibaba.fastjson.JSONArray;
-import com.light.Util.GithubConstant;
-import com.light.Util.HttpsUtil;
+import com.light.util.GithubConstant;
+import com.light.util.HttpsUtil;
 import org.springframework.stereotype.Controller;
 import org.springframework.ui.Model;
 import org.springframework.util.StringUtils;

### 2021-09-01 Java/src/main/java/com/light/controllers/HelloController.java

@@ -1,5 +1,10 @@
 package com.light.controllers;
 
+import com.light.repository.MainRepository;
+
+import org.slf4j.Logger;
+import org.slf4j.LoggerFactory;
+import org.springframework.beans.factory.annotation.Autowired;
 import org.springframework.stereotype.Controller;
 import org.springframework.ui.Model;
 import org.springframework.web.bind.annotation.GetMapping;
@@ -9,10 +14,22 @@ import org.springframework.web.bind.annotation.RequestParam;
 @Controller
 @RequestMapping("/")
 public class HelloController {
+
+    private final MainRepository mainRepository;
+    Logger logger = LoggerFactory.getLogger(this.getClass());
+
     @GetMapping("/")
     public String hello(Model model, @RequestParam(value="name", required=false, defaultValue="World") String name) {
         model.addAttribute("name", name);
+        long cnt = mainRepository.count();
+        logger.debug("get from db:" + cnt);
         return "hello";
     }
+
+    @Autowired
+    private HelloController(MainRepository mainRepository) {
+        this.mainRepository = mainRepository;
+    }
+
 }
 

### 2021-09-01 Java/src/main/java/com/light/entity/MainObj.java

@@ -1,0 +1,86 @@
+package com.light.entity;
+
+import java.util.Date;
+
+import javax.persistence.Column;
+import javax.persistence.Entity;
+import javax.persistence.Id;
+import javax.persistence.Table;
+
+
+@Entity
+@Table(name = "main")
+public class MainObj {
+    @Id
+    private Long id;
+
+    @Column(name = "datetime")
+    private Date datetime;
+
+    private String radiance;
+
+    private int pixels;
+
+    private int cityId;
+
+    private String window;
+
+    private String file;
+
+    public Date getDatetime() {
+        return datetime;
+    }
+
+    public Long getId() {
+        return id;
+    }
+
+    public void setId(Long id) {
+        this.id = id;
+    }
+
+    public String getFile() {
+        return file;
+    }
+
+    public void setFile(String file) {
+        this.file = file;
+    }
+
+    public String getWindow() {
+        return window;
+    }
+
+    public void setWindow(String window) {
+        this.window = window;
+    }
+
+    public int getCityId() {
+        return cityId;
+    }
+
+    public void setCityId(int cityId) {
+        this.cityId = cityId;
+    }
+
+    public int getPixels() {
+        return pixels;
+    }
+
+    public void setPixels(int pixels) {
+        this.pixels = pixels;
+    }
+
+    public String getRadiance() {
+        return radiance;
+    }
+
+    public void setRadiance(String radiance) {
+        this.radiance = radiance;
+    }
+
+    public void setDatetime(Date datetime) {
+        this.datetime = datetime;
+    }
+ 
+}

### 2021-09-01 Java/src/main/java/com/light/repository/MainRepository.java

@@ -1,0 +1,15 @@
+package com.light.repository;
+
+
+import org.springframework.data.repository.CrudRepository;
+import org.springframework.stereotype.Repository;
+
+import java.util.List;
+
+import com.light.entity.MainObj;
+
+@Repository
+public interface MainRepository extends CrudRepository<MainObj, Long> {
+
+    List<MainObj> findAll();
+}

### 2021-09-01 data/processor/crawler.py

@@ -2,6 +2,8 @@ import os
 import json
 import boto3
 from urllib.request import urlopen
+
+from mysql.connector import catch23
 from file_utils import FileUtils
 from sns_processor import process
 
@@ -15,9 +17,13 @@ wait_area = FileUtils.WAIT_LIST
 native_run = FileUtils.native_run
 
 def url_to_json(url: str):
-    with urlopen(url) as furl:
-        content = furl.read()
-    return json.loads(content)
+    try:
+        with urlopen(url) as furl:
+            content = furl.read()
+            return json.loads(content)
+    except Exception as e:
+        print('[ERROR] url load error:{}'.format(url))
+    
 
 def get_links(catalog: json, url: str):
     children = list()

### 2021-09-01 Java/src/main/java/com/light/controllers/HelloController.java
get json  data from main table

@@ -1,10 +1,15 @@
 package com.light.controllers;
 
+import java.util.List;
+
+import com.light.entity.MainObj;
 import com.light.repository.MainRepository;
 
 import org.slf4j.Logger;
 import org.slf4j.LoggerFactory;
 import org.springframework.beans.factory.annotation.Autowired;
+import org.springframework.http.HttpStatus;
+import org.springframework.http.ResponseEntity;
 import org.springframework.stereotype.Controller;
 import org.springframework.ui.Model;
 import org.springframework.web.bind.annotation.GetMapping;
@@ -24,6 +29,14 @@ public class HelloController {
         long cnt = mainRepository.count();
         logger.debug("get from db:" + cnt);
         return "hello";
+    }
+
+    @GetMapping("/city")
+    public ResponseEntity<List<MainObj>> getMainObjByCityId(Model model, @RequestParam(value="id", required=true, defaultValue="0") Integer cityId) {
+        long cnt = mainRepository.count();
+        logger.debug("get from db:" + cnt);
+        List<MainObj> lst = mainRepository.findByCityId(cityId);
+        return new ResponseEntity<List<MainObj>>(lst, HttpStatus.OK);
     }
 
     @Autowired

### 2021-09-01 Java/src/main/java/com/light/entity/MainObj.java

@@ -7,6 +7,7 @@ import javax.persistence.Entity;
 import javax.persistence.Id;
 import javax.persistence.Table;
 
+import com.fasterxml.jackson.annotation.JsonIgnore;
 
 @Entity
 @Table(name = "main")
@@ -25,6 +26,7 @@ public class MainObj {
 
     private String window;
 
+    @JsonIgnore
     private String file;
 
     public Date getDatetime() {

### 2021-09-01 Java/src/main/java/com/light/repository/MainRepository.java

@@ -12,4 +12,6 @@ import com.light.entity.MainObj;
 public interface MainRepository extends CrudRepository<MainObj, Long> {
 
     List<MainObj> findAll();
+
+    List<MainObj> findByCityId(Integer cityId);
 }

### 2021-09-02 data/processor/crawler.py
fix nz bug

@@ -55,7 +55,7 @@ def native_handle_sqs(event, context):
     for record in records:    
         url = record['body']
         print('[INFO] process filename:{}'.format(url))
-        if url.__contains__('/201204/'):
+        if url.__contains__('/201204/') or url.__contains__('/201205/') or url.__contains__('/201206/'):
             print('[INFO] {} already process!'.format(url))
             continue
         catalog = url_to_json(url)

### 2021-09-03 paper/main.tex
paper and ppt

@@
 \documentclass[conference]{IEEEtran}
-\usepackage[utf8]{inputenc}
+\IEEEoverridecommandlockouts
+% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
 
-\title{COMPX527 Assignment 1 Report}
+\usepackage{amsmath,amssymb,amsfonts}
+\usepackage{algorithmic}
+\usepackage{graphicx} 
+\usepackage{textcomp}
+\usepackage{xcolor}
+\bibliographystyle{IEEEtran}
+\usepackage[backend=biber,doi=true, natbib=true ]{biblatex}
+\addbibresource{main.bib}
 
-\author{
-\IEEEauthorblockN{Glenn Cumming}
-\IEEEauthorblockA{Department of Computer Science\\
-  \textit{University of Waikato}\\
-  Hamilton, New Zealand\\
-  \texttt{glenn@hif.nz}}
+\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
+    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+\begin{document}
+
+\title{Earth at night*\\
+{\footnotesize \textsuperscript{*}The visualisation of average radiance in specific area}
+}
+
+\author{\IEEEauthorblockN{1\textsuperscript{st} Zhen Chen}
+\IEEEauthorblockA{\textit{Faculty of Computing and Mathematical Sciences} \\
+\textit{The University of Waikato}\\
+Beijing, China \\
+1561010}
 \and
-\IEEEauthorblockN{Mitchell Grout}
-\IEEEauthorblockA{Department of Computer Science\\
-  \textit{University of Waikato}\\
-  Hamilton, New Zealand\\
-  \texttt{mjg44@students.waikato.ac.nz}}
+\IEEEauthorblockN{2\textsuperscript{nd} Huajie Xu}
+\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+\textit{name of organization (of Aff.)}\\
+City, Country \\
+email address or ORCID}
 \and
-\IEEEauthorblockN{Shufen Li}
-\IEEEauthorblockA{Department of Computer Science\\
-  \textit{University of Waikato}\\
-  Hamilton, New Zealand\\
-  \texttt{sl302@students.waikato.ac.nz}}
+\IEEEauthorblockN{3\textsuperscript{rd} Shengzhu Wang}
+\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+\textit{name of organization (of Aff.)}\\
+City, Country \\
+email address or ORCID}
 \and
-\IEEEauthorblockN{Sunny Chikara}
-\IEEEauthorblockA{Department of Computer Science\\
-  \textit{University of Waikato}\\
-  Hamilton, New Zealand\\
-  \texttt{sc420@students.waikato.ac.nz}}
+\IEEEauthorblockN{4\textsuperscript{th} Wenjie Tong}
+\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+\textit{name of organization (of Aff.)}\\
+City, Country \\
+email address or ORCID}
 \and
-\IEEEauthorblockN{YingJun Huang}
-\IEEEauthorblockA{Department of Computer Science\\
-  \textit{University of Waikato}\\
-  Hamilton, New Zealand\\
-  \texttt{yh320@students.waikato.ac.nz}}
+\IEEEauthorblockN{5\textsuperscript{th} SiXiang Xiong}
+\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+\textit{name of organization (of Aff.)}\\
+City, Country \\
+email address or ORCID}
 }
-\begin{document}
 
@@
 \begin{abstract}
-We designed an Object Detection web service on the AWS Cloud Provider, using Terraform for programmable infrastrucure, Ansible for deployment, and Python for the web service and object detection.
+This document is the description about the solution of Assignment 2 of Compx527 paper in Waikato University.
+World Bank Nightime Light Data consists of a lot of satellite imagery from the Visible Infrared Imaging Radiometer Suite Day-Night Band (VIIRS DNB) from 2012-2020.
+We choose 3 specific areas all over the world and focus on the imagery of these places.
+From these imagery, we can learn the trend of their radiance in the period.
+Some articles shows that the night light represents the development in the same area.
+We can preview the economic development of areas by the trend.
 \end{abstract}
+
 \begin{IEEEkeywords}
-AWS, COMPX527, Terraform, Ansible, Flask, Python, Object Detection, Retinanet
+Night light, STAC, COG, VIIRS DNB, AWS
 \end{IEEEkeywords}
+
 \section{Solution Summary}
-The Flask Object Detection service is a load balanced HTTP service deployed in AWS EC2, using the AWS ELB load balancer.
-The service can accept a JPG image and run object detection on it, and returns the resulting image with identified objects highlighted.
-\section{Motivation}
-We decided on object detection in the cloud in order to learn and appricate the challenges of providing a stateless, scalbale service that could be used for a variey of other projects.
-Examples included
+A lot of things are depended by our project.
+It is important that imagery from AWS open datasets has almost not processed too much before storing.
+So we have to spend too much time on the data.
+To ensure our project development, we use Lark, which is a kind of instant messenger in China used in office, to record documents and communicate in a group.
+A sumary about our solution is shown as below.
+
+\subsection{Open Nighttime Lights}
+this is the explaination  \cite{BARA2020106658}
+
+\subsection{Frontend}
+this is the explanation
+
+\subsection{vue}
+this is the explanation
+
+\subsection{D3}
+this is the explanation
+
+\subsection{spring-boot}
+this is the explanation
+
+\subsection{oauth github}
+this is the explanation
+
+\subsection{ansible}
+this is the explanation
+
+\subsection{CloudFormation}
+this is the explanation
+
+\subsection{nginx/tomcat}
+this is the explanation
+
+\subsection{RDS/Lambda/secrets manager/SQS/EC2}
+this is the explanation
+
+\section{Proposed solution}
+
+\subsection{Whole structure}
+A architecture pic.
+
+\subsection{Frontend}
+
+\subsection{Login}
+
+\subsection{Data processing}
+
+\subsection{Testing}
+
+\subsection{Project management}
+
+\section{Security Considerations}
+
+\subsection{Networking}
+
+\subsection{User}
+
+\subsection{IAM}
+
+\section{Team members and individual contribution within the team}
 \begin{itemize}
-\item Contexutal threat analysis, such as humans detected in an area which should only include livestock.
-\item Numbercial anyalisis, such as the number of a species of wildlife in an area over time.
-\item Absence detection, indetifying objects that should be in an image but are not
-\end{itemize}
-\section{Proposed Solution}
-An Amazon Web Services based cluster of web servers taking images from clients and returning images with bionding boxed indetified objects plus json formatted data, behind an Eleastic Load Balancer.
-The cluster will be horizontally scalable by adding web servers, and accessable via curl or any other HTTP client that can perform HTTP POST requests.
-It was trained used the AWS COCO data set \footnote{https://registry.opendata.aws/fast-ai-coco/}, and also used the set to for testing and demonstrations.
-\section{Solution Architecture}
-We decided to use a load balanced web service architecture, a very common and well understood model with common solutions to scalability and uptime. We have the following components and features:
-\subsection{The Image Processing Server}
-The project uses the Retinanet based Object Detection developed by Keras
-\footnote{https://github.com/fizyr/keras-retinanet}. The web service was developed in Python using a Flask server \footnote{https://pypi.org/project/Flask/}.\par
-The server recives via HTTP JPG formatted image, and returns the image with bounding boxes around identified objects, plus JSON data of the images.
-\subsection{The Load Balancer}
-The object detection being inhernetly slow forces the use of laod balancing and scaling techniques.
-Using the AWS Elastic Load Balancer allowed us balance the HTTP requests over two or more EC2 servers running the Flask servers.
-We could create as many Flask servers as we wished, although of course this lent itself to waisted compute resources.
-Though we had great sucess early on using AWS AutoScaling Groups, which allows a lower and upper limit of EC2 instances running our Flask server to be defined, this functionality was not avalible in the student accounts.
-\subsection{The Web User Interface}
-In order to have a better demo, it was decided to go ahead and produce a web site interface that would allow uploading 
-\subsection{The Web API}
-The intended standard way to interact with the Flask Object Detection Cluster is to access it via HTTP calls using the url http://\textless load\_balancer\_fqdn\textgreater/detect.
-As the system is inteneded for the use of non-private images no ssl was implemented on the load balancer, though it is supported.
-\subsection{Amazon Web Services Cloud}
-The service running on the Amazon Web Services Cloud, the required choice of the assignment.
-Though later in lectures there it wa smentioned we could look in to using other Cloud Service Providers, we decied we had already made enough progress to commit ourselves to AWS for this project.
-Though we did use terraform, which supports IaaS deployments with mulitple CSP, in case we had a need to effect a change quickly.
-
-\section{Technology}
-The following are the significant technologies we used in this assignment.
-\subsection{Retinanet}
-Retinanet is an open source object detection neural net. This technology was chosen for the following reasons \footnote{}.
-\begin{itemize}
-\item Free Open Source project obviously beneficial for a project with a limited budget.
-\item Python 3 for rapid development and deploymewnt. With a mix of experinced and less experinced team members this was particulary useful.
-\item Specific instructions using it with the dataset avaliable on the Registry of Open Data on AWS \footnote{https://registry.opendata.aws/fast-ai-coco/}
-\end{itemize}
-\subsection{Terraform}
-Terraform was given in as an example of the provisioning service to use in this assignment.
-AWS CloudFormation was another option suggested.
-The decision to go with terraform rather than CloudFormation was based on the following
-\begin{itemize}
-  \item CloudFormation is prioritory and is specific to AWS cloud offierings.
-Though this assigmnet is on a small and temporty scale, we still not want to use a technology that would create vendor lockin
-  \item Terraform supports provisioning many different platforms, both open standards and priopritary, such as Azure, Goolge Cloud, Kubernetes and OpenStack \footnote{https://aws.amazon.com/cloudformation/}.
-Developng expericne in deployments with terraform therefore was demied to be more useful.
-\end{itemize}
-\subsection{Ansible}
-Though Terraform is capable of running commands post-install in order to install services and other software needed for our cluster, our cluster used Ansible playbooks instead.
-Though it meant learning another technology, we demeed a good use of our time since:
-\begin{itemize}
-  \item Terraform can only run scripts, which would have to be created.
-  \item Ansible's langauge is very flxible and is created specifally for the purpose of delpoymnet.
-  \item This is a recommended approach by HashiCorp, the devlopers of Terraform. \footnote{https://www.hashicorp.com/resources/ansible-terraform-better-together}
+    \item Zhen Chen:  PM, BE, DevOps
+    \item Huajie Xu: FE
+    \item Shengzhu Wang(Simon): BE
+    \item SiXiang Xiong(Tom): BE, Testing
+    \item Wenjie Tong: Data Researcher, Testing
 \end{itemize}
 
-\subsection{Github}
-We used github for source control of all documents and code.
-This was chosen over other solutions suc h as SVN and Mecurial due to the familiarity of some of the team members with git.
-Others in our team have leanrt cloning, pulling and branching.
-\footnote{https://github.com/}
-\subsection{Slack}
-As we needed to communicate effectively over a period of weeks without seeing each other often, we decided to use the colloberation software Slack \footnote{https://slack.com/}.
-We used a free account, and created a channel to allow us to privately communicate about our work.
-It was used extensively and allowed constant effecteive communication.
-\subsection{Trello}
-In ordr to break up and manage tasks we created a Kanban Board in Trello \footnote{https://trello.com/}.
-This got us started with basic learning and setup tasks early on, but as the project progressed we tended to move to the use of Slack to define and assign tasks and workloads.
-\subsection{LaTex}
-LaTex \footnote{https://www.latex-project.org/} is the accepted standard for scientific papers; therefore although the assignment pointed us to the IEEE A4 standard for reporting, we opted to use the LaTex standard.
-This gave us very useful experince in using LaTex for proper report formatting.
-This report was created in LaTex using the IEEEtran document class provided by IEEE template avaliable at
-\footnote{https://www.ieee.org/conferences/publishing/templates.html}
-, and generated into PDF by Gnome LaTeX
-\footnote{https://wiki.gnome.org/Apps/GNOME-LaTeX}
-\subsection{Flask}
-The decision to develop and depoly a service using the keras-retinanet Python library immediately suggested to us we should again use Python to provide the web service.
-Our team had develpoers with experince in both Tornado and Flask; Flask was used as the web service development fell on the person with Flask experince.
-Both solutions would have been suitable.
-\section{Existing object detection soltutions}
-There is a wide range of cloud and non cloud solutions. A comparison of these to our own solution is beyound the scope of this document. Those provided by the large Cloud Service Providers includes:
-\subsection{Rekognition}
-Amazon's object detection solution \footnote{https://aws.amazon.com/rekognition/}.
-\subsection{Vision AI}
-Google's object detection solution \footnote{https://cloud.google.com/vision/}.
-\subsection{Computer Vision}
-Microsofts object detection solution \footnote{https://azure.microsoft.com/en-us/services/\\cognitive-services/computer-vision/}.
+\subsection{Equations}
+Number equations consecutively. To make your 
+equations more compact, you may use the solidus (~/~), the exp function, or 
+appropriate exponents. Italicize Roman symbols for quantities and variables, 
+but not Greek symbols. Use a long dash rather than a hyphen for a minus 
+sign. Punctuate equations with commas or periods when they are part of a 
+sentence, as in:
+\begin{equation}
+a+b=\gamma\label{eq}
+\end{equation}
 
-\section{Security and Vunlerability Assessment}
-\subsection{Data Security}
-The Flask Object Detection Cluster was specifically created to be stateless and public.
-Interception of HTTP requests and results can be easily interceptied by third parties with access to the networks between the client and the service.
-Users of the service should be aware that any images sent or data recived from the service could be illictly obtained, mallicously modified, or corrupted in transit.
-\par
-Migtigation could be acheived by adding SSL encryption and offloading it at the load balancer.
-\subsection{Access Security}
-\paragraph{Identity and Access Management}
-Management access of the resources residing on AWS is protected via the AWS Identity and Access Management (IAM) system \footnote{https://docs.aws.amazon.com/IAM/latest/UserGuide/introduction.html}.
-We used individual accounts provided by the course.
-If an account was compromised the it would allow malicous actors to shut down services, or replace the current services with malacoius alternatives.
-For example, they cloud replace an instance with one that will return malware embeded in an image.
-\par
-Mitigation can be using good protection practices for authentication information, Two Factor Auth (2FA), regular monitoring of the service with a set of well known HTTP requests checked against expected results.
-\paragraph{Server Access}
-The Flask servers are publically accessable via SSH, needed for deployment.
-If the key pair is compromised or the keys obtained then root access to the Flask servers cloud be obtained.
-This would grant the attacker full acccess and the ability to use the server's resources for there own purposes.
-\par
-Migragtion can be using ssh key passwords, encrypted storage of the keys, checking server hashes, and keeping ssh software up to date with security patches.
-\subsection{Network Security}
-We used AWS Security Groups to restrict the Load Balancer to only ingress traffic port 80. The Image Processers restricted to port 22 and 80. \par
-Allowing direct access to the service port is a known problem that could allow an attaacker to easily DDOS a single server, bypassing the Load Balancer.
-To mitigate this we need to work out how to define the CIDR range in the security group to match the internal IP of the Load Balancer.
-The service is load banced, but we where not able to use AutoScaling Groups due to our account restrictions.
-This results in having to manually create additional servers to cope with increased requests, and so a DDOS would be more effective since a human will have to respond to any such attack.\par
-To mitigate this we should move to an account that allows the use of Auto Scaling Groups.  
-\subsection{Monitoring and Security}
-AWS EC2 instance monitoring was enabled during the terraform creation of the cluster.
-ELB monitors the avalibility of the Flask HTTP servers.
-The lack of external monitoring means that we are totally dependent on AWS for security checks and uptime monitoring.
-\par
-Mitigation of the lack of monitoring is obviousloy acheived by using both in house and monitoring services.
-Common examples of in house monioring is via Nagios, Icinga2, Munin and Promethues.
-Monitoring services include Uptime.com \footnote{https://uptime.com/uptime-monitoring} for ping and HTTP monitoring, and Paessler \footnote{https://www.paessler.com/port\_monitoring}, which provides addiotnal services such as port monitoring.
+Be sure that the 
+symbols in your equation have been defined before or immediately following 
+the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
+the beginning of a sentence: ``Equation \eqref{eq} is . . .''
 
-\section{Actual AWS Expenditure}
-TODO
-\section{Future Improvements}
-\paragraph{Packaging}
-Deployment scripts were chosen for deployment and running the services.
-However, if the service was to be developed further we would being to use stdeb \footnote{https://pypi.org/project/stdeb/} for packaging for the Ubuntu servers, and potentially set up a Personal Package Archive \footnote{https://help.ubuntu.com/community/PPA}.
-This would ensure futher development and upgrades by making it part of the standard apt package management system.
-\paragraph{Service Management}
-Currently the starting and stopping of the service is done via control scripts. These would be integrated in to systemd service management \footnote{https://wiki.debian.org/systemd}.
-\paragraph{HTTP}
-The service is stateless, plublic and insecure.
-If a layer of security is desired to protect the data in transit, then HTTPS can be added to the Elastic Load Balancer via the AWS Certificate Manager \footnote{https://docs.aws.amazon.com/elasticloadbalancing\\/latest/classic/ssl-server-cert.html}.
-The simple reason for not using this was cost: we would have to pay for extra services when our budget was tight.
-\paragraph{Cloudflare Multi Region Load Balancing}
-Redeployment of the service changes the FQDN in the URL.
-Also, the service is currenlty deployed on only one region.
-The Cloudflare Load Balancing would allow the use of many regions or in fact many Cloud Providers to be used with a single contant url presented to the send consumer.
-The fact that the service is stateless makes it very suitable to this form of scale out \footnote{https://www.cloudflare.com/load-balancing/}
-\paragraph{Monitoring}
-Future development of the cluster would likely use additional monitoring of performance, costs and uptimes using dedicated EC2 instances, and such existing monitoring systems as Icinga2, Promethues and Munin.
-Uptime moniroing would of nessescity be run etxernally, such as on internal machines or another cloud providers offering.
-\par
-We would also start to use third party external monitoring services such as Uptime.com \footnote{https://uptime.com/uptime-monitoring} or Paessler \footnote{https://www.paessler.com/}
-\section{Team Members Contributions}
-\section{Assignment Requirements Completion}
-The requirements for this Assignment were communicated in serveral ways, including the assignment documentation, messages in the Moodle channel, the lectures, and by asking the lectuerer and asistant directly.
-We treated these as customer reuirements, which typically start with a good understanding of the desired outcomes and often require feedback from the customer to ensure we are achiving them.\par
-The following is what we have determine dto be the requirements, and how we have achived each one.
+\subsection{\LaTeX-Specific Advice}
+
+Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
+of ``hard'' references (e.g., \verb|(1)|). That will make it possible
+to combine sections, add equations, or change the order of figures or
+citations without having to go through the file line by line.
+
+Please don't use the \verb|{eqnarray}| equation environment. Use
+\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
+environment leaves unsightly spaces around relation symbols.
+
+Please note that the \verb|{subequations}| environment in {\LaTeX}
+will increment the main equation counter even when there are no
+equation numbers displayed. If you forget that, you might write an
+article in which the equation numbers skip from (17) to (20), causing
+the copy editors to wonder if you've discovered a new method of
+counting.
+
+{\BibTeX} does not work by magic. It doesn't get the bibliographic
+data from thin air but from .bib files. If you use {\BibTeX} to produce a
+bibliography you must send the .bib files.
+
+{\LaTeX} can't read your mind. If you assign the same label to a
+subsubsection and a table, you might find that Table I has been cross
+referenced as Table IV-B3.
+
+{\LaTeX} does not have precognitive abilities. If you put a
+\verb|\label| command before the command that updates the counter it's
+supposed to be using, the label will pick up the last counter to be
+cross referenced instead. In particular, a \verb|\label| command
+should not go before the caption of a figure or a table.
+
+Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
+will not stop equation numbers inside \verb|{array}| (there won't be
+any anyway) and it might stop a wanted equation number in the
+surrounding equation.
+
+\subsection{Some Common Mistakes}\label{SCM}
 \begin{itemize}
-  \item Use of AWS to create a non-trivial service, demonstrating our understanding of cloud technologies, their use, and their challenges.
-  \item Use of technologies such as Terraform, Ansible and Cloud Formation for programmably defined infrastructure and depoyments
-  \item Use of a open dataset from AWS
-  \item Work within a team with very diverse technical backgrounds and manage them to ensure fair distribution of the work.
+\item The word ``data'' is plural, not singular.
+\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
+\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
+When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
+A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
+(A parenthetical sentence is punctuated within the parentheses.)
+\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
+\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
+\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
+\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
+\item Do not confuse ``imply'' and ``infer''.
+\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
+\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
+\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
 \end{itemize}
-.
+
+\subsection{Authors and Affiliations}
+\textbf{The class file is designed for, but not limited to, six authors.} A 
+minimum of one author is required for all conference articles. Author names 
+should be listed starting from left to right and then moving down to the 
+next line. This is the author sequence that will be used in future citations 
+and by indexing services. Names should not be listed in columns nor group by 
+affiliation. Please keep your affiliations as succinct as possible (for 
+example, do not differentiate among departments of the same organization).
+
+\subsection{Identify the Headings}
+Headings, or heads, are organizational devices that guide the reader through 
+your paper. There are two types: component heads and text heads.
+
+Component heads identify the different components of your paper and are not 
+topically subordinate to each other. Examples include Acknowledgments and 
+References and, for these, the correct style to use is ``Heading 5''. Use 
+``figure caption'' for your Figure captions, and ``table head'' for your 
+table title. Run-in heads, such as ``Abstract'', will require you to apply a 
+style (in this case, italic) in addition to the style provided by the drop 
+down menu to differentiate the head from the text.
+
+Text heads organize the topics on a relational, hierarchical basis. For 
+example, the paper title is the primary text head because all subsequent 
+material relates and elaborates on this one topic. If there are two or more 
+sub-topics, the next level head (uppercase Roman numerals) should be used 
+and, conversely, if there are not at least two sub-topics, then no subheads 
+should be introduced.
+
+\subsection{Figures and Tables}
+\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
+bottom of columns. Avoid placing them in the middle of columns. Large 
+figures and tables may span across both columns. Figure captions should be 
+below the figures; table heads should appear above the tables. Insert 
+figures and tables after they are cited in the text. Use the abbreviation 
+``Fig.~\ref{fig}'', even at the beginning of a sentence.
+
+\begin{table}[htbp]
+\caption{Table Type Styles}
+\begin{center}
+\begin{tabular}{|c|c|c|c|}
+\hline
+\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
+\cline{2-4} 
+\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
+\hline
+copy& More table copy$^{\mathrm{a}}$& &  \\
+\hline
+\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
+\end{tabular}
+\label{tab1}
+\end{center}
+\end{table}
+
+\begin{figure}[htbp]
+\centerline{\includegraphics{fig1.png}}
+\caption{Example of a figure caption.}
+\label{fig}
+\end{figure}
+
+Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
+rather than symbols or abbreviations when writing Figure axis labels to 
+avoid confusing the reader. As an example, write the quantity 
+``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
+units in the label, present them within parentheses. Do not label axes only 
+with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
+\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
+quantities and units. For example, write ``Temperature (K)'', not 
+``Temperature/K''.
+
+\section*{Acknowledgment}
+
+The preferred spelling of the word ``acknowledgment'' in America is without 
+an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
+G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
+acknowledgments in the unnumbered footnote on the first page.
+
+\section*{References}
+
+Number footnotes separately in superscripts. Place the actual footnote at 
+the bottom of the column in which it was cited. Do not put footnotes in the 
+abstract or reference list. Use letters for table footnotes.
+
+Unless there are six authors or more give all authors' names; do not use 
+``et al.''. Papers that have not been published, even if they have been
+
+\printbibliography
+
+\vspace{12pt}
+\color{red}
+IEEE conference templates contain guidance text for composing and formatting conference papers.
+Please ensure that all template text is removed from your conference paper prior to submission to the conference.
+Failure to remove the template text from your paper may result in your paper not being published.
+
 \end{document}

### 2021-09-03 Frontend/dist/static/js/app.0db8ce1c34d2ce4e03d9.js
1.add dist directory 2.show real data in line chart

@@ -1,0 +1,2 @@
+webpackJsonp([1],{0:function(t,e){},"4Zy+":function(t,e){},Bdqv:function(t,e){},Ch8T:function(t,e){},I6Vy:function(t,e){},NHnr:function(t,e,n){"use strict";Object.defineProperty(e,"__esModule",{value:!0});var a=n("7+uW"),i={render:function(){var t=this.$createElement,e=this._self._c||t;return e("div",{attrs:{id:"app"}},[e("router-view")],1)},staticRenderFns:[]};var s=n("VU/8")({name:"app"},i,!1,function(t){n("4Zy+")},null,null).exports,r=n("/ocq"),o=n("ifoU"),l=n.n(o),c={render:function(){this.$createElement;this._self._c;return this._m(0)},staticRenderFns:[function(){var t=this.$createElement,e=this._self._c||t;return e("footer",{staticClass:"footer-7 text-center-xs"},[e("div",{staticClass:"container"},[e("div",{staticClass:"row"},[e("div",{staticClass:"col-sm-6"},[e("span",{staticClass:"type--fine-print"},[this._v("© "),e("span",{staticClass:"update-year"}),this._v(" A2Inc — All Rights\n                    Reserved")])])])])])}]},d=n("VU/8")(null,c,!1,null,null,null).exports,u=n("vRTy"),h={props:["initialData"],data:function(){return{data:this.initialData,width:600,height:400,scaleX:null,scaleY:null,path:null,line:null,svg:null,xAxis:null,gXAxis:null,yAxis:null,gYAxis:null,margin:{top:20,right:20,bottom:30,left:30}}},methods:{draw:function(){var t=this;null==this.svg&&(this.svg=u.m("div.line_chart").append("svg").attr("viewBox",[0,0,this.width,this.height]).style("overflow","visible"),this.scaleX=u.l().domain(u.d(this.data.dates)).range([this.margin.left,this.width-this.margin.right]),this.scaleY=u.k().domain([0,u.g(this.data.series,function(t){return u.g(t.values)})]).nice().range([this.height-this.margin.bottom,this.margin.top]),this.line=u.f().defined(function(t){return!isNaN(t)}).x(function(e,n){return t.scaleX(t.data.dates[n])}).y(function(e){return t.scaleY(e)}),this.xAxis=function(e){return e.attr("transform","translate(0,"+(t.height-t.margin.bottom)+")").call(u.a(t.scaleX).ticks(t.width/80).tic
[…]

### 2021-09-03 Frontend/src/router/index.js

@@ -5,6 +5,7 @@ import Login from '@/components/Login'
 import Redirect from '@/components/Redirect'
 import TestD3 from '@/components/TestD3'
 import MultiLineChart from '@/components/MultiLineChart'
+import TestEmptyPage from '@/components/TestEmptyPage'
 
 Vue.use(Router)
 
@@ -38,6 +39,11 @@ export default new Router({
             path: '/test/line_chart',
             name: 'TestLineChart',
             component: MultiLineChart
+        },
+        {
+            path: '/test/empty',
+            name: 'TestEmptyPage',
+            component: TestEmptyPage
         }
     ]
 })

### 2021-09-03 paper/main.tex

@@
 % The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-
+\usepackage{cite}
 \usepackage{amsmath,amssymb,amsfonts}
@@
 \usepackage{xcolor}
-\bibliographystyle{IEEEtran}
-\usepackage[backend=biber,doi=true, natbib=true ]{biblatex}
-\addbibresource{main.bib}
-
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 \and
-\IEEEauthorblockN{2\textsuperscript{nd} Huajie Xu}
+\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
 \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
@@
 \and
-\IEEEauthorblockN{3\textsuperscript{rd} Shengzhu Wang}
+\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
 \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
@@
 \and
-\IEEEauthorblockN{4\textsuperscript{th} Wenjie Tong}
+\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
 \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
@@
 \and
-\IEEEauthorblockN{5\textsuperscript{th} SiXiang Xiong}
+\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
 \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
@@
 From these imagery, we can learn the trend of their radiance in the period.
-Some articles shows that the night light represents the development in the same area.
+Some articles shows that the night light represented the development in the same area.
 We can preview the economic development of areas by the trend.
@@
 \begin{IEEEkeywords}
-Night light, STAC, COG, VIIRS DNB, AWS
+Night light, STAC, COG, VIIRS DNB, aws
 \end{IEEEkeywords}
 
-\section{Solution Summary}
-A lot of things are depended by our project.
-It is important that imagery from AWS open datasets has almost not processed too much before storing.
-So we have to spend too much time on the data.
-To ensure our project development, we use Lark, which is a kind of instant messenger in China used in office, to record documents and communicate in a group.
-A sumary about our solution is shown as below.
+\section{Introduction}
+This document is a model and instructions for \LaTeX.
+Please observe the conference page limits.
 
-\subsection{Open Nighttime Lights}
-this is the explaination  \cite{BARA2020106658}
+\section{Ease of Use}
 
-\subsection{Frontend}
-this is the explanation
+\subsection{Maintaining the Integrity of the Specifications}
 
-\subsection{vue}
-this is the explanation
+The IEEEtran class file is used to format your paper and style the text. All margins, 
+column widths, line spaces, and text fonts are prescribed; please do not 
+alter them. You may note peculiarities. For example, the head margin
+measures proportionately more than is customary. This measurement 
+and others are deliberate, using specifications that anticipate your paper 
+as one part of the entire proceedings, and not as an independent document. 
+Please do not revise any of the current designations.
 
-\subsection{D3}
-this is the explanation
+\section{Prepare Your Paper Before Styling}
+Before you begin to format your paper, first write and save the content as a 
+separate text file. Complete all content and organizational editing before 
+formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
+proofreading, spelling and grammar.
 
-\subsection{spring-boot}
-this is the explanation
+Keep your text and graphic files separate until after the text has been 
+formatted and styled. Do not number text heads---{\LaTeX} will do that 
+for you.
 
-\subsection{oauth github}
-this is the explanation
+\subsection{Abbreviations and Acronyms}\label{AA}
+Define abbreviations and acronyms the first time they are used in the text, 
+even after they have been defined in the abstract. Abbreviations such as 
+IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
+abbreviations in the title or heads unless they are unavoidable.
 
-\subsection{ansible}
-this is the explanation
-
-\subsection{CloudFormation}
-this is the explanation
-
-\subsection{nginx/tomcat}
-this is the explanation
-
-\subsection{RDS/Lambda/secrets manager/SQS/EC2}
-this is the explanation
-
-\section{Proposed solution}
-
-\subsection{Whole structure}
-A architecture pic.
-
-\subsection{Frontend}
-
-\subsection{Login}
-
-\subsection{Data processing}
-
-\subsection{Testing}
-
-\subsection{Project management}
-
-\section{Security Considerations}
-
-\subsection{Networking}
-
-\subsection{User}
-
-\subsection{IAM}
-
-\section{Team members and individual contribution within the team}
+\subsection{Units}
 \begin{itemize}
-    \item Zhen Chen:  PM, BE, DevOps
-    \item Huajie Xu: FE
-    \item Shengzhu Wang(Simon): BE
-    \item SiXiang Xiong(Tom): BE, Testing
-    \item Wenjie Tong: Data Researcher, Testing
+\item Use either SI (MKS) or CGS as primary units.
+(SI units are encouraged.) English units may be used as secondary units (in parentheses).
+An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
+\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
+This often leads to confusion because equations do not balance dimensionally.
+If you must use mixed units, clearly state the units for each quantity that you use in an equation.
+\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
+Spell out units when they appear in text: ``.
+.
+.
+a few henries'', not ``.
+.
+.
+a few H''.
+\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
 \end{itemize}
@@
 \end{itemize}
+An excellent style manual for science writers is \cite{b7}.
 
@@
 
+Please number citations consecutively within brackets \cite{b1}. The 
+sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
+number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
+the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
+
 Number footnotes separately in superscripts. Place the actual footnote at 
@@
 ``et al.''. Papers that have not been published, even if they have been 
+submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
+that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
+Capitalize only the first word in a paper title, except for proper nouns and 
+element symbols.
 
-\printbibliography
+For papers published in translation journals, please give the English 
+citation first, followed by the original foreign-language citation \cite{b6}.
 
+\begin{thebibliography}{00}
+\bibitem{b1} G.
+Eason, B.
+Noble, and I.
+N.
+Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil.
+Trans.
+Roy.
+Soc.
+London, vol.
+A247, pp.
+529--551, April 1955.
+\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
+\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
+\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
+\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
+\bibitem{b6} Y.
+Yorozu, M.
+Hirano, K.
+Oka, and Y.
+Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
+J.
+Magn.
+Japan, vol.
+2, pp.
+740--741, August 1987 [Digests 9th Annual Conf.
+Magnetics Japan, p.
+301, 1982].
+\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
+\end{thebibliography}
 \vspace{12pt}

### 2021-09-04 Frontend/config/index.js
set different deploymode

@@ -25,6 +25,13 @@ module.exports = {
                 pathRewrite: {
                     '^/github': ''
                 }
+            },
+            '/awselb': {
+                target: 'http://httpelb-1499061197.ap-southeast-1.elb.amazonaws.com/',
+                changeOrigin: true,
+                pathRewrite: {
+                    '^/awselb': ''
+                }
             }
         },
 

### 2021-09-04 Java/src/main/java/com/light/controllers/AppErrorController.java
404 > / for vue

@@ -1,0 +1,23 @@
+package com.light.controllers;
+
+import org.springframework.boot.web.servlet.error.ErrorController;
+import org.springframework.http.HttpStatus;
+import org.springframework.stereotype.Controller;
+import org.springframework.web.bind.annotation.RequestMapping;
+import org.springframework.web.bind.annotation.ResponseBody;
+import org.springframework.web.bind.annotation.ResponseStatus;
+import org.springframework.web.servlet.ModelAndView;
+import org.springframework.web.servlet.view.RedirectView;
+@Controller
+@ResponseStatus(HttpStatus.MOVED_PERMANENTLY)
+public class AppErrorController implements ErrorController{
+    private final static String PATH = "/error";
+    @RequestMapping(PATH)
+    @ResponseBody
+    public ModelAndView getErrorPath() {
+        RedirectView red = new RedirectView("/",true);
+        red.setStatusCode(HttpStatus.MOVED_PERMANENTLY);
+        return new ModelAndView(red);
+    }
+
+}

### 2021-09-04 Java/src/main/java/com/light/controllers/AppErrorController.java
fix bug:http code 200

@@ -14,6 +14,7 @@ public class AppErrorController implements ErrorController{
     private final static String PATH = "/error";
     @RequestMapping(PATH)
     @ResponseBody
+    @ResponseStatus(HttpStatus.OK)
     public ModelAndView getErrorPath() {
         InternalResourceView red = new InternalResourceView("/",true);
         //red.setStatusCode(HttpStatus.MOVED_PERMANENTLY);

### 2021-09-04 Frontend/config/index.js
reset redirect function

@@ -73,6 +73,7 @@ module.exports = {
         // Paths
         assetsRoot: path.resolve(__dirname, '../dist'),
         assetsSubDirectory: 'static',
+        //assetsPublicPath: '/',
         assetsPublicPath: '/',
 
         /**

### 2021-09-04 Frontend/dist/static/js/app.4c25687daa9a72fc8fe1.js

@@ -1,2 +1,0 @@
-webpackJsonp([1],{0:function(t,e){},"4Zy+":function(t,e){},Bdqv:function(t,e){},Ch8T:function(t,e){},HiFG:function(t,e){},NHnr:function(t,e,n){"use strict";Object.defineProperty(e,"__esModule",{value:!0});var a=n("7+uW"),i={render:function(){var t=this.$createElement,e=this._self._c||t;return e("div",{attrs:{id:"app"}},[e("router-view")],1)},staticRenderFns:[]};var s=n("VU/8")({name:"app"},i,!1,function(t){n("4Zy+")},null,null).exports,r=n("/ocq"),o=n("ifoU"),l=n.n(o),c={render:function(){this.$createElement;this._self._c;return this._m(0)},staticRenderFns:[function(){var t=this.$createElement,e=this._self._c||t;return e("footer",{staticClass:"footer-7 text-center-xs"},[e("div",{staticClass:"container"},[e("div",{staticClass:"row"},[e("div",{staticClass:"col-sm-6"},[e("span",{staticClass:"type--fine-print"},[this._v("© "),e("span",{staticClass:"update-year"}),this._v(" A2Inc — All Rights\n                    Reserved")])])])])])}]},d=n("VU/8")(null,c,!1,null,null,null).exports,u=n("vRTy"),h={props:["initialData"],data:function(){return{data:this.initialData,width:600,height:400,scaleX:null,scaleY:null,path:null,line:null,svg:null,xAxis:null,gXAxis:null,yAxis:null,gYAxis:null,margin:{top:20,right:20,bottom:30,left:30}}},methods:{draw:function(){var t=this;null==this.svg&&(this.svg=u.m("div.line_chart").append("svg").attr("viewBox",[0,0,this.width,this.height]).style("overflow","visible"),this.scaleX=u.l().domain(u.d(this.data.dates)).range([this.margin.left,this.width-this.margin.right]),this.scaleY=u.k().domain([0,u.g(this.data.series,function(t){return u.g(t.values)})]).nice().range([this.height-this.margin.bottom,this.margin.top]),this.line=u.f().defined(function(t){return!isNaN(t)}).x(function(e,n){return t.scaleX(t.data.dates[n])}).y(function(e){return t.scaleY(e)}),this.xAxis=function(e){return e.attr("transform","translate(0,"+(t.height-t.margin.bottom)+")").call(u.a(t.scaleX).ticks(t.width/80).t
[…]

### 2021-09-04 Java/src/main/java/com/light/controllers/GithubLogController.java
oauth api

@@ -1,16 +1,22 @@
 package com.light.controllers;
 
-
 import com.alibaba.fastjson.JSONArray;
 import com.light.util.GithubConstant;
 import com.light.util.HttpsUtil;
+
+import org.slf4j.Logger;
+import org.slf4j.LoggerFactory;
+import org.springframework.http.HttpStatus;
+import org.springframework.http.ResponseEntity;
 import org.springframework.stereotype.Controller;
 import org.springframework.ui.Model;
-import org.springframework.util.StringUtils;
-//import org.apache.commons.lang3.StringUtils;
+// import org.springframework.util.StringUtils;
+import org.apache.commons.lang3.StringUtils;
 import org.springframework.web.bind.annotation.RequestMapping;
 
 import javax.servlet.http.HttpServletRequest;
+import javax.servlet.http.HttpSession;
+
 import java.util.Arrays;
 import java.util.HashMap;
 import java.util.Map;
@@ -18,74 +24,146 @@ import java.util.Map;
 @Controller
 public class GithubLogController {
 
-//    @Autowired
-//    private IGithubService githubService;
-    //The callback address
+    private Logger logger = LoggerFactory.getLogger(this.getClass());
+    // @Autowired
+    // private IGithubService githubService;
+    // The callback address
     @RequestMapping("/oauth/redirect")
-    public String callback(String code, String state, Model model, HttpServletRequest req) throws Exception{
-        System.out.println(code);
-/*        public static boolean hasText(@Nullable String str) {
-              return (str != null && !str.isEmpty() && containsText(str));
-        }*/
-        if (StringUtils.hasText(code) && StringUtils.hasText(state)){
+    public String callback(String code, String state, Model model, HttpServletRequest req) throws Exception {
+        logger.debug(code);
+        /*
+         * public static boolean hasText(@Nullable String str) { return (str != null &&
+         * !str.isEmpty() && containsText(str)); }
+         */
+        if (StringUtils.isNotBlank(code) && StringUtils.isNotBlank(state)) {
             HttpsUtil http = new HttpsUtil();
-            //Request a token through code
-            String token_url = GithubConstant.TOKEN_URL.replace("CODE",code);
-            //Put the String into the map
+            // Request a token through code
+            String token_url = GithubConstant.TOKEN_URL.replace("CODE", code);
+            // Put the String into the map
             String responseStr = http.doGetForString(token_url);
             Map<String, Object> resMap = urlStringToMap(responseStr);
[…]

### 2021-09-04 paper/main.tex
fix @RequestMapping("/awselb")

--- 2021-09-03 paper/main.tex
@@
 
+\usepackage[T1]{fontenc} 
 \usepackage{amsmath,amssymb,amsfonts}
@@
 \usepackage{xcolor} 
-\bibliographystyle{IEEEtran}
-\usepackage[backend=biber,doi=true, natbib=true ]{biblatex}
-\addbibresource{main.bib}
+% \bibliographystyle{IEEEtran} 
+% \usepackage[backend=biber,doi=true, natbib=true ]{biblatex}
+% \addbibresource{main.bib}
 
@@
      T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+
 \begin{document}
@@
 \subsection{Open Nighttime Lights}
-this is the explaination  \cite{BARA2020106658}
+% this is the explaination  \cite{BARA2020106658}
 
@@
 \subsection{ansible}
-this is the explanation
+Ansible is a famous open source deployment platform. Most of services in AWS can be working rightly with Ansible. We used it for our main sctructure deployment.
 
 \subsection{CloudFormation}
-this is the explanation
+CloudFormation is a service in AWS, which can organize our service very quickly and no codes need to write.
+The configuration in CloudFormation is a template which is just a yaml file.
+It is more convient than Ansible for some services.
+We use it deploy the RDS and Lambda Service.
 
 \subsection{nginx/tomcat}
-this is the explanation
+Nginx
 
@@
 
-\printbibliography
+% \printbibliography
 

### 2021-09-04 paper/main.tex
main tex

@@
 \usepackage{xcolor} 
-% \bibliographystyle{IEEEtran} 
-% \usepackage[backend=biber,doi=true, natbib=true ]{biblatex}
-% \addbibresource{main.bib}
+\bibliographystyle{IEEEtran} 
+\usepackage[backend=bibtex,doi=true, natbib=true ]{biblatex}
+\addbibresource{main.bib}
 
@@
 \subsection{Open Nighttime Lights}
-% this is the explaination  \cite{BARA2020106658}
+this is the explaination  \cite{BARA2020106658}
 
@@
 \subsection{nginx/tomcat}
-Nginx
+Nginx is the widely used web server all over the world.
+It also has the excellent performance as a reverse proxy.
+We use it as our fontend server.
+Tomcat is a tranditional Java web container supporting Java Servlet.
+Our Java code run on Tomcat.
 
 \subsection{RDS/Lambda/secrets manager/SQS/EC2}
-this is the explanation
+These items are the name of services on AWS.
+Especially, we use Lambda to generate temperary password of RDS, and store it in Secrets Manager.
+It is a good method to enhance the security of database password.
 
@@
 
-% \printbibliography
+\printbibliography
 

### 2021-09-05 Java/src/main/java/com/light/Util/GithubConstant.java
new oauth id

@@ -2,9 +2,9 @@ package com.light.util;
 
 public class GithubConstant {
 
-    public static final String CLIENT_ID="952b74100002a9ff5430";
+    public static final String CLIENT_ID="c04fa22c7aa981ba6419";
 
-    public static final String CLIENT_SECRET="b7021233ca275c55c68dd1b19b3702b20e871dc3";
+    public static final String CLIENT_SECRET="bdb66391bf8b1eff8f18fc84357cfabedfe03e4c";
 
     public static final String CALLBACK = "http://localhost:8888/oauth/redirect";
 

### 2021-09-05 data/processor/crawler.py

@@ -55,7 +55,7 @@ def native_handle_sqs(event, context):
     for record in records:    
         url = record['body']
         print('[INFO] process filename:{}'.format(url))
-        if url.__contains__('/201208/') or url.__contains__('/201209/') or url.__contains__('/201204/') or url.__contains__('/201205/') or url.__contains__('/201206/') or url.__contains__('/201207/'):
+        if url.__contains__('/201209/') or url.__contains__('/201210/') or url.__contains__('/201208/') or url.__contains__('/201209/') or url.__contains__('/201204/') or url.__contains__('/201205/') or url.__contains__('/201206/') or url.__contains__('/201207/'):
             print('[INFO] {} already process!'.format(url))
             continue
         catalog = url_to_json(url)

### 2021-09-05 Java/src/main/java/com/light/Util/GithubConstant.java
token

@@ -4,13 +4,11 @@ public class GithubConstant {
 
     public static final String CLIENT_ID="c04fa22c7aa981ba6419";
 
-    public static final String CLIENT_SECRET="bdb66391bf8b1eff8f18fc84357cfabedfe03e4c";
-
     public static final String CALLBACK = "http://localhost:8888/oauth/redirect";
 
     public static final String CODE_URL = "https://github.com/login/oauth/authorize?client_id="+CLIENT_ID+"state=STATE&redirect_uri="+CALLBACK+"";
 
-    public static final String TOKEN_URL = "https://github.com/login/oauth/access_token?client_id="+CLIENT_ID+"&client_secret="+CLIENT_SECRET+"&code=CODE&redirect_uri="+CALLBACK+"";
+    public static final String TOKEN_URL = "https://github.com/login/oauth/access_token?client_id="+CLIENT_ID+"&client_secret=CLIENT_SECRET&code=CODE&redirect_uri="+CALLBACK+"";
 
     public static final String USER_INFO_URL = "https://api.gihub.com/user/repos?access_token=TOKEN";
 

### 2021-09-05 Java/src/main/java/com/light/Util/GithubConstant.java
fix token

@@ -3,8 +3,8 @@ package com.light.util;
 public class GithubConstant {
 
     public static final String CLIENT_ID="c04fa22c7aa981ba6419";
-
-    public static final String CALLBACK = "http://localhost:8888/oauth/redirect";
+    //https://github.com/login/oauth/authorize?client_id=c04fa22c7aa981ba6419&redirect_uri=http%3A%2F%2Fhttpelb-1499061197.ap-southeast-1.elb.amazonaws.com%2Foauth%2Fredirect&scope=read%3Auser&state=A2Inc
+    public static final String CALLBACK = "http://httpelb-1499061197.ap-southeast-1.elb.amazonaws.com/oauth/redirect";
 
     public static final String CODE_URL = "https://github.com/login/oauth/authorize?client_id="+CLIENT_ID+"state=STATE&redirect_uri="+CALLBACK+"";
 

### 2021-09-05 Java/src/main/java/com/light/controllers/GithubLogController.java

@@ -126,11 +126,11 @@ public class GithubLogController {
     }
 
     @RequestMapping("/oauth/token")
-    public ResponseEntity<Map<String,String>> token(String code, String state, Model model, HttpServletRequest req, HttpSession session) throws Exception {
-        Map<String,String> map = new HashMap<>();
+    public ResponseEntity<Map<String,Object>> token(String code, String state, Model model, HttpServletRequest req, HttpSession session) throws Exception {
+        Map<String,Object> map = new HashMap<>();
         if (! StringUtils.isNotBlank(code) ||  !StringUtils.isNotBlank(state)) {
             map.put("r", "no token");
-            return new ResponseEntity<Map<String,String>>(map,HttpStatus.NON_AUTHORITATIVE_INFORMATION);
+            return new ResponseEntity<Map<String,Object>>(map,HttpStatus.NON_AUTHORITATIVE_INFORMATION);
         }
         HttpsUtil http = new HttpsUtil();
         String token_url = GithubConstant.TOKEN_URL.replace("CODE", code).replace("CLIENT_SECRET", getSecret());
@@ -138,8 +138,11 @@ public class GithubLogController {
         Map<String, Object> resMap = urlStringToMap(responseStr);
             
         if (resMap.get("access_token") == null) {
+            if (resMap.get("error") != null) {
+                map.put("desc", resMap.get("error").toString());
+            }
             map.put("r", "error code");
-            return new ResponseEntity<Map<String,String>>(map,HttpStatus.NON_AUTHORITATIVE_INFORMATION);
+            return new ResponseEntity<Map<String,Object>>(map,HttpStatus.NON_AUTHORITATIVE_INFORMATION);
         }
         // //Access Token
         String token = resMap.get("access_token").toString();
@@ -157,11 +160,8 @@ public class GithubLogController {
         session.setAttribute("code", code);
         session.setAttribute("token", token);
         map.put("token", token);
-        map.put("user", responseStr);
-        
-        
-
-        return new ResponseEntity<Map<String,String>>(map,HttpStatus.OK);
+        map.put("user", JSONArray.parse(responseStr));
+        return new ResponseEntity<Map<String,Object>>(map,HttpStatus.OK);
     }
 
     @RequestMapping("/oauth/islogin")

### 2021-09-05 Frontend/build/webpack.dev.conf.js
still debugging 3rd party login

@@ -14,82 +14,83 @@ const HOST = process.env.HOST
 const PORT = process.env.PORT && Number(process.env.PORT)
 
 const devWebpackConfig = merge(baseWebpackConfig, {
-  module: {
-    rules: utils.styleLoaders({ sourceMap: config.dev.cssSourceMap, usePostCSS: true })
-  },
-  // cheap-module-eval-source-map is faster for development
-  devtool: config.dev.devtool,
-
-  // these devServer options should be customized in /config/index.js
-  devServer: {
-    clientLogLevel: 'warning',
-    historyApiFallback: {
-      rewrites: [
-        { from: /.*/, to: path.posix.join(config.dev.assetsPublicPath, 'index.html') },
-      ],
+    module: {
+        rules: utils.styleLoaders({ sourceMap: config.dev.cssSourceMap, usePostCSS: true })
     },
-    hot: true,
-    contentBase: false, // since we use CopyWebpackPlugin.
-    compress: true,
-    host: HOST || config.dev.host,
-    port: PORT || config.dev.port,
-    open: config.dev.autoOpenBrowser,
-    overlay: config.dev.errorOverlay
-      ? { warnings: false, errors: true }
-      : false,
-    publicPath: config.dev.assetsPublicPath,
-    proxy: config.dev.proxyTable,
-    quiet: true, // necessary for FriendlyErrorsPlugin
-    watchOptions: {
-      poll: config.dev.poll,
-    }
-  },
-  plugins: [
-    new webpack.DefinePlugin({
-      'process.env': require('../config/dev.env')
-    }),
-    new webpack.HotModuleReplacementPlugin(),
-    new webpack.NamedModulesPlugin(), // HMR shows correct file names in console on update.
-    new webpack.NoEmitOnErrorsPlugin(),
-    // https://github.com/ampedandwired/html-webpack-plugin
-    new HtmlWebpackPlugin({
-      filename: 'index.html',
-      template: 'index.html',
-      inject: true
-    }),
-    // copy custom static assets
-    new CopyWebpackPlugin([
-      {
-        from: path.resolve(__dirname, '../static'),
-        to: config.dev.assetsSubDirectory,
-        ignore: ['.*']
-      }
-    ])
-  ]
+    // cheap-module-eval-source-map is faster for development
+    devtool: config.dev.devtool,
+
+    // these devServer options should be customized in /config/index.js
+    devServer: {
+        disableHostCheck: true, //disable host check
[…]

### 2021-09-05 Frontend/config/index.js

@@ -6,7 +6,6 @@ const path = require('path')
 
 module.exports = {
     dev: {
-
         // Paths
         assetsSubDirectory: 'static',
         assetsPublicPath: '/',
@@ -37,7 +36,7 @@ module.exports = {
 
         // Various Dev Server settings
         host: 'localhost', // can be overwritten by process.env.HOST
-        port: 8888, // can be overwritten by process.env.PORT, if port is in use, a free one will be determined
+        port: 80, // can be overwritten by process.env.PORT, if port is in use, a free one will be determined
         autoOpenBrowser: false,
         errorOverlay: true,
         notifyOnErrors: true,

### 2021-09-05 Frontend/src/main.js

@@ -15,11 +15,21 @@ Vue.prototype.$querystring = querystring
 Vue.use(VueResource)
 
 Vue.config.productionTip = false
+Vue.http.options.emulateJSON = true
+
+// setting
+Vue.prototype.$deployMode = 0 // 0 local 1 ali 2 aws
 
 /* eslint-disable no-new */
 
-function fakeAuth () {
+function auth () {
     if (sessionStorage['token'] != null) {
+        /*
+        this.$http.post('/awselb/oauth/islogin', { token: code, state: 'A2inc' }).then((response) => {
+            console.log(response.body)
+        }, (response) => {
+            console.error(response)
+        }) */
         return true
     } else {
         return false
@@ -27,7 +37,7 @@ function fakeAuth () {
 }
 
 router.beforeEach((to, from, next) => {
-    if (to.meta.requireAuth && !fakeAuth()) {
+    if (to.meta.requireAuth && !auth()) {
         // Check login state
         next({ path: '/login' })
     } else {

### 2021-09-05 paper/main.tex
fix ieee format
paper

@@
 
-\usepackage[T1]{fontenc} 
 \usepackage{amsmath,amssymb,amsfonts}
@@
 \usepackage{xcolor} 
-\bibliographystyle{IEEEtran} 
-\usepackage[backend=bibtex,doi=true, natbib=true ]{biblatex}
+\usepackage[backend=biber]{biblatex}
 \addbibresource{main.bib}
@@
 This document is the description about the solution of Assignment 2 of Compx527 paper in Waikato University.
-World Bank Nightime Light Data consists of a lot of satellite imagery from the Visible Infrared Imaging Radiometer Suite Day-Night Band (VIIRS DNB) from 2012-2020.
-We choose 3 specific areas all over the world and focus on the imagery of these places.
-From these imagery, we can learn the trend of their radiance in the period.
-Some articles shows that the night light represents the development in the same area.
-We can preview the economic development of areas by the trend.
+World Bank Nightime Light Data consists of a lot of satellite imagery stored in Amazon Web Services (AWS).
+Recent files from 2012-2020 are generated by the sensors named Visible Infrared Imaging Radiometer Suite Day-Night Band (VIIRS DNB).
+All the things are stored by Cloud Optimized GeoTIFF (COG) format and organized by Spatial Temporal Asset Catalog (STAC) standard.
+This project only researches the imagery from 3 specific areas.
+From them, you can learn the trend of their radiance in the period.
+It is also a good chance to have a better understanding of ecnomic trend by them.
 \end{abstract}
@@
 \section{Solution Summary}
-A lot of things are depended by our project.
-It is important that imagery from AWS open datasets has almost not processed too much before storing.
-So we have to spend too much time on the data.
-To ensure our project development, we use Lark, which is a kind of instant messenger in China used in office, to record documents and communicate in a group.
-A sumary about our solution is shown as below.
+A lot of services are depended by this project.
+It is important to know that imagery from AWS open datasets has almost not processed too much before storing.
+So the Geospatial Data Abstraction Library (GDAL) is imported for the complicated computing.
+In addition, to ensure our project development schedule, Lark, which is a kind of instant messenger used in Chinese office, is used to record documents and communicate in a group.
+The architecture of our solution is shown as below.
+
+\begin{figure}[htbp]
+    \centerline{\includegraphics[width=260pt]{images/arch.png}}
+    \caption{Architecture}
+    \label{fig1}
+\end{figure}
+
+Figure Labels: To process the S3 data, two Lambda functions are generated.
+One is to follow the STAC protcol to find the imagery, and another is to analyse the picture by GDAL, which is a kind of high cost computation.
+There are more than 4 pictures per day per area, and more than 5,000 pictures per month totally.
+All the result processed by Lambda is stored in RDS and synced from us-east-1 region to ap-southeast-1 region.
+In addition, the password of MySQL are generated by a Lambda function and rotated timely.
+So the development team do not need to copy the password.
+Any feature with the password have to get it from Secrets Manager.
+
+When it comes to show the result in ap-southeast-1 region, networking security is the most essential thing because this part of service can be touched by end users.
+So except ELB server and deployment server, there are not any other servers with public ip.
+All the EC2 can visit public network from the NAT, but public network can not visit them directly.
 
@@
 \subsection{ansible}
-Ansible is a famous open source deployment platform. Most of services in AWS can be working rightly with Ansible. We used it for our main sctructure deployment.
+Ansible is a famous open source deployment platform.
 

### 2021-09-05 paper/main.tex
paper

@@
 \begin{abstract}
-This document is the description about the solution of Assignment 2 of Compx527 paper in Waikato University.
-World Bank Nightime Light Data consists of a lot of satellite imagery stored in Amazon Web Services (AWS).
-Recent files from 2012-2020 are generated by the sensors named Visible Infrared Imaging Radiometer Suite Day-Night Band (VIIRS DNB).
-All the things are stored by Cloud Optimized GeoTIFF (COG) format and organized by Spatial Temporal Asset Catalog (STAC) standard.
-This project only researches the imagery from 3 specific areas.
-From them, you can learn the trend of their radiance in the period.
-It is also a good chance to have a better understanding of ecnomic trend by them.
+This document is the description about the solution for Assignment 2 of Compx527 paper 
+in Waikato University. World Bank Nightime Light Data consists of a lot of satellite imagery 
+stored in Amazon Web Services (AWS). Recent files from 2012 to 2020 are generated by the sensor 
+named Visible Infrared Imaging Radiometer Suite Day-Night Band (VIIRS DNB) \cite{WorldBan13:online}. All these things are 
+stored by Cloud Optimized GeoTIFF (COG) \cite{CloudOpt5:online} format and organized by Spatial Temporal Asset Catalog (STAC) standard \cite{SpatioTe90:online}. 
+This project only need the imagery in 3 specific areas, but it is neccessary to process all of them. 
+From them, you can learn the trend of their radiance in the period. It is also a good chance to have a better understanding of ecnomic trend by them.
+Some researchers also try to find the light pollution by this kind of data \cite{BARA2020106658}.
 \end{abstract}
@@
 \section{Solution Summary}
-A lot of services are depended by this project.
-It is important to know that imagery from AWS open datasets has almost not processed too much before storing.
-So the Geospatial Data Abstraction Library (GDAL) is imported for the complicated computing.
-In addition, to ensure our project development schedule, Lark, which is a kind of instant messenger used in Chinese office, is used to record documents and communicate in a group.
-The architecture of our solution is shown as below.
+A lot of services are depended by this project. It is important to know that imagery from AWS open datasets 
+has almost not processed too much before being stored. So the Geospatial Data Abstraction Library (GDAL) is 
+imported for the complicated computing. GDAL is a common open source library used for various geospatial data formats \cite{GDAL—GDA74:online}. 
+In this project, it is the translator from raster file to vector. So that it is possible to calculate the insection area 
+between the satellite imagery and the target area. All of the imagery is the orignal file from the satellite, so
+the bad weather would impact the real data, i.e. cloudy and some other atmosphere issues. The project objective is 
+to learn the AWS usage and security practice, to get more real data as the reality, more research on how to identify 
+cloud and bad weather still need to be done. These bad cases would be influence this project demo very obivously.
+
+In addition, to ensure the development schedule, Lark, which is a kind of instant messenger used in Chinese office, 
+is used to record documents and communicate in a group. At the first day, all team members were divided into 7 roles, i.e. project manager,
+backend engineer, frontend engineer, devops, testing and data researcher. The project plan was made instantly when everybody understanding
+the features, see Fig.~\ref{fig1}.
+
+\begin{figure}[htbp]
+    \centerline{\includegraphics[width=260pt]{images/plan.png}}
+    \caption{Project schedule}
+    \label{fig1}
+\end{figure}
+
+Agile development project management method was used in this project. So the team has a short video meeting everyday. This plan is the last 
+result after several development iterations.
+
+The architecture of our solution is shown as Fig.~\ref{fig2}. Both of security and budget are important. So a network address translation (NAT) gateway 
+was used for the essential network design. But after two days, NAT had to close because of the budget alert. But it is neccessary that hiding the 
+internal services into the internal network instead of exposing them to the internet.
+
+There are two important methods to keep the passowrd safely. The first one is IAM role. IAM role provides good security protection in the whole structure.
+Different IAM roles are generated to attach to different Lambda functions. The execution roles are granted permission of access to necessary AWS services. 
+There are some common policies for them, e.g. AWSLambdaBasicExecutionRole and AmazonS3FullAccess policies. The second one is Secrets Manager service in AWS.
+All of the passwords in this project are stored in it. Visiting it through Secrets Manager when needed.
 
@@
     \caption{Architecture}
-    \label{fig1}
+    \label{fig2}
 \end{figure}
 
-Figure Labels: To process the S3 data, two Lambda functions are generated.
-One is to follow the STAC protcol to find the imagery, and another is to analyse the picture by GDAL, which is a kind of high cost computation.
-There are more than 4 pictures per day per area, and more than 5,000 pictures per month totally.
-All the result processed by Lambda is stored in RDS and synced from us-east-1 region to ap-southeast-1 region.
-In addition, the password of MySQL are generated by a Lambda function and rotated timely.
-So the development team do not need to copy the password.
-Any feature with the password have to get it from Secrets Manager.
+To process the S3 data, two Lambda functions are generated. One is to follow the STAC protcol to find the imagery, and another is to analyse pictures by GDAL, 
+which is a kind of high cost computation in AWS. There are more than 4 pictures per day per area, and about 5,000 pictures per month totally. All the result processed by 
+Lambda is stored in RDS and synced from us-east-1 region to ap-southeast-1 region. In addition, the password of MySQL is generated by a Lambda function and rotated 
+timely. So the development team do not need to copy the password. Any features with passwords have to get it from Secrets Manager.
 
-When it comes to show the result in ap-southeast-1 region, networking security is the most essential thing because this part of service can be touched by end users.
-So except ELB server and deployment server, there are not any other servers with public ip.
-All the EC2 can visit public network from the NAT, but public network can not visit them directly.
+When it comes to show the result in ap-southeast-1 region, network security is the most essential thing because this part of service can be touched by end users. 
+So except ELB and the deployment server, there are not any other servers with public IP. All the EC2 instances can visit public network from the NAT, but public network 
+can not visit them directly.
+
+To explain more steps, there are some summaries as below.
 
@@
 
-\subsection{vue}
+\subsection{Vue}
 this is the explanation
@@
 
-\subsection{spring-boot}
+\subsection{Spring-boot}
 this is the explanation
 
-\subsection{oauth github}
+\subsection{Oauth github}
 this is the explanation
 
-\subsection{ansible}
-Ansible is a famous open source deployment platform.
+\subsection{Ansible}
+Ansible is a famous open source deployment platform, which is convenient to enable the infrastructure as code. 
+It is the main tool to deploy most of the services in this project. Especially, a single EC2 instance with public 
+IP is provided for it. But AWS service has to provision services by aws-cli instead of Ansible itself. There are still 
+some libaries providing these functions but mostly are from external part.
 
 \subsection{CloudFormation}
-CloudFormation is a service in AWS, which can organize our service very quickly and no codes need to write.
-The configuration in CloudFormation is a template which is just a yaml file.
-It is more convient than Ansible for some services.
-We use it deploy the RDS and Lambda Service.
+CloudFormation is a service in AWS, which can organize services very quickly and configure them by yaml or json. There area
+several templates for provisioning different services. It is more convient than Ansible for some services. In this project, 
+RDS and Lambda Services are dependent on it.
 
-\subsection{nginx/tomcat}
-Nginx is the widely used web server all over the world.
-It also has the excellent performance as a reverse proxy.
-We use it as our fontend server.
-Tomcat is a tranditional Java web container supporting Java Servlet.
-Our Java code run on Tomcat.
+\subsection{Nginx/Tomcat}
+Nginx is the widely used web server all over the world. It also has the excellent performance as a reverse proxy. 
+Fontend server is the role in this project. Tomcat, which is behind Nginx, is a tranditional Java web container supporting 
+Java Servlet. The visualisation is deisgned by Java and run in this container. Both Nginx and Tomcat are well-known because of 
+the open source community and internet companies choosing.
 
-\subsection{RDS/Lambda/secrets manager/SQS/EC2}
-These items are the name of services on AWS.
-Especially, we use Lambda to generate temperary password of RDS, and store it in Secrets Manager.
-It is a good method to enhance the security of database password.
+\subsection{RDS/Lambda/Secrets Manager/SQS/EC2/NAT}
+These items are names of services on AWS. Especially, Lambda are used to generate temperary password of RDS, and store it in 
+Secrets Manager. It is really a good method to enhance the security for the password of database. On the other hand, NAT is a 
+good feature for isolating the internal and external networks, but the price is too high to be used all the time in this project.
 
@@
 
-\subsection{Whole structure}
-A architecture pic.
+A demo has finished all of tasks following the plan on time in this project. But to save budget, stoping NAT and processing parts of data are 
+the temporary approaches. It is also possible to deal with the cloud and other disruption to ensure the accrute radiance value. All the 
+other details are described as below.
+
+\subsection{Whole infrastructure}
+The main architecture is shown as Fig.~\ref{fig2}.
 
@@
 
-\subsection{Equations}
-Number equations consecutively. To make your 
-equations more compact, you may use the solidus (~/~), the exp function, or 
-appropriate exponents. Italicize Roman symbols for quantities and variables, 
-but not Greek symbols. Use a long dash rather than a hyphen for a minus 
-sign. Punctuate equations with commas or periods when they are part of a 
-sentence, as in:
-\begin{equation}
-a+b=\gamma\label{eq}
-\end{equation}
-
-Be sure that the 
-symbols in your equation have been defined before or immediately following 
-the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
-the beginning of a sentence: ``Equation \eqref{eq} is . . .''
-
-\subsection{\LaTeX-Specific Advice}
-
-Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-to combine sections, add equations, or change the order of figures or
-citations without having to go through the file line by line.
-
-Please don't use the \verb|{eqnarray}| equation environment. Use
-\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-environment leaves unsightly spaces around relation symbols.
-
-Please note that the \verb|{subequations}| environment in {\LaTeX}
-will increment the main equation counter even when there are no
-equation numbers displayed. If you forget that, you might write an
-article in which the equation numbers skip from (17) to (20), causing
-the copy editors to wonder if you've discovered a new method of
-counting.
-
-{\BibTeX} does not work by magic. It doesn't get the bibliographic
-data from thin air but from .bib files. If you use {\BibTeX} to produce a
-bibliography you must send the .bib files.
-
-{\LaTeX} can't read your mind. If you assign the same label to a
-subsubsection and a table, you might find that Table I has been cross
-referenced as Table IV-B3.
-
-{\LaTeX} does not have precognitive abilities. If you put a
-\verb|\label| command before the command that updates the counter it's
-supposed to be using, the label will pick up the last counter to be
-cross referenced instead. In particular, a \verb|\label| command
-should not go before the caption of a figure or a table.
-
-Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-will not stop equation numbers inside \verb|{array}| (there won't be
-any anyway) and it might stop a wanted equation number in the
-surrounding equation.
-
-\subsection{Some Common Mistakes}\label{SCM}
-\begin{itemize}
-\item The word ``data'' is plural, not singular.
-\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-\item Do not confuse ``imply'' and ``infer''.
-\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-\end{itemize}
-
-\subsection{Authors and Affiliations}
-\textbf{The class file is designed for, but not limited to, six authors.} A 
-minimum of one author is required for all conference articles. Author names 
-should be listed starting from left to right and then moving down to the 
-next line. This is the author sequence that will be used in future citations 
-and by indexing services. Names should not be listed in columns nor group by 
-affiliation. Please keep your affiliations as succinct as possible (for 
-example, do not differentiate among departments of the same organization).
-
-\subsection{Identify the Headings}
-Headings, or heads, are organizational devices that guide the reader through 
-your paper. There are two types: component heads and text heads.
-
-Component heads identify the different components of your paper and are not 
-topically subordinate to each other. Examples include Acknowledgments and 
-References and, for these, the correct style to use is ``Heading 5''. Use 
-``figure caption'' for your Figure captions, and ``table head'' for your 
-table title. Run-in heads, such as ``Abstract'', will require you to apply a 
-style (in this case, italic) in addition to the style provided by the drop 
-down menu to differentiate the head from the text.
-
-Text heads organize the topics on a relational, hierarchical basis. For 
-example, the paper title is the primary text head because all subsequent 
-material relates and elaborates on this one topic. If there are two or more 
-sub-topics, the next level head (uppercase Roman numerals) should be used 
-and, conversely, if there are not at least two sub-topics, then no subheads 
-should be introduced.
-
 \subsection{Figures and Tables}
-\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
-bottom of columns. Avoid placing them in the middle of columns. Large 
-figures and tables may span across both columns. Figure captions should be 
-below the figures; table heads should appear above the tables. Insert 
-figures and tables after they are cited in the text. Use the abbreviation 
+ Use the abbreviation 
 ``Fig.~\ref{fig}'', even at the beginning of a sentence.
@@
 
-Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
-rather than symbols or abbreviations when writing Figure axis labels to 
-avoid confusing the reader. As an example, write the quantity 
-``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
-units in the label, present them within parentheses. Do not label axes only 
-with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
-\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
-quantities and units. For example, write ``Temperature (K)'', not 
-``Temperature/K''.
-
-\section*{Acknowledgment}
-
-The preferred spelling of the word ``acknowledgment'' in America is without 
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-acknowledgments in the unnumbered footnote on the first page.
-
-\section*{References}
-
-Number footnotes separately in superscripts. Place the actual footnote at 
-the bottom of the column in which it was cited. Do not put footnotes in the 
-abstract or reference list. Use letters for table footnotes.
-
-Unless there are six authors or more give all authors' names; do not use 
-``et al.''. Papers that have not been published, even if they have been
-
 \printbibliography
 
-\vspace{12pt}
-\color{red}
-IEEE conference templates contain guidance text for composing and formatting conference papers.
-Please ensure that all template text is removed from your conference paper prior to submission to the conference.
-Failure to remove the template text from your paper may result in your paper not being published.
-
 \end{document}

### 2021-09-06 Frontend/config/index.js
basically completed login debugging

@@ -12,7 +12,7 @@ module.exports = {
         //proxyTable: {},
         proxyTable: {
             '/api': {
-                target: 'http://localhost:8080',
+                target: 'http://localhost:8080/awselb',
                 changeOrigin: true,
                 pathRewrite: {
                     '^/api': ''

### 2021-09-06 Frontend/src/global.js

@@ -1,0 +1,12 @@
+const deployMode = 2 // 0 local 1 ali 2 aws
+// const apiHead = '/api' // '/api' local '/awselb' awselb
+const apiHead = '/awselb'
+const state = 'A2Inc'
+const tokenStorageType = 1 // 0 sessionStorage 1 localStorage
+
+export default {
+    deployMode,
+    apiHead,
+    state,
+    tokenStorageType
+}

### 2021-09-06 Frontend/src/main.js

@@ -11,35 +11,46 @@ import '@/assets/css/custom.css'
 
 // premise
 import VueResource from 'vue-resource'
+import global from './global.js'
 Vue.prototype.$querystring = querystring
 Vue.use(VueResource)
 
 Vue.config.productionTip = false
 Vue.http.options.emulateJSON = true
 
-// setting
-Vue.prototype.$deployMode = 0 // 0 local 1 ali 2 aws
+// global setting
+Vue.prototype.$global = global
 
 /* eslint-disable no-new */
 
-function auth () {
-    if (sessionStorage['token'] != null) {
-        /*
-        this.$http.post('/awselb/oauth/islogin', { token: code, state: 'A2inc' }).then((response) => {
-            console.log(response.body)
-        }, (response) => {
-            console.error(response)
-        }) */
-        return true
-    } else {
-        return false
-    }
-}
-
 router.beforeEach((to, from, next) => {
-    if (to.meta.requireAuth && !auth()) {
-        // Check login state
-        next({ path: '/login' })
+    if (to.matched.some(m => m.meta.requireAuth)) { // if need login
+        if (to.name === 'Login') {
+            next()
+        } else {
+            let token
+            if (global.tokenStorageType === 0) {
+                token = sessionStorage.getItem('token')
+            } else {
+                token = localStorage.getItem('token')
+            }
+            if (token != null) {
+                Vue.http.post(global.apiHead + '/oauth/islogin', { token, state: global.state }).then((response) => {
+                    console.log(response.body)
+                    if (response.body.r === 'OK') {
+                        next()
+                    } else {
+                        alert('r: ' + response.body.r)
+                        next('/Login')
+                    }
+                }, (response) => {
+                    alert(response)
+                    next('/Login')
+                })
+            } else {
+                next('/Login')
+            }
+        }
     } else {
         next()
     }

### 2021-09-06 paper/main.tex
paper update

@@
 \subsection{Ansible}
-Ansible is a famous open source deployment platform, which is convenient to enable the infrastructure as code. 
+Ansible is a famous open source deployment platform, which is convenient to enable the infrastructure as code (IaC). 
 It is the main tool to deploy most of the services in this project. Especially, a single EC2 instance with public 
@@
 \subsection{Whole infrastructure}
-The main architecture is shown as Fig.~\ref{fig2}.
+The main architecture is shown as Fig.~\ref{fig2}. First of all, two kinds of IaC platform, which are Ansible and CloudFormation.
+Ansible is the first choice that can be esily used in most of situations. When some service need to configure complicatedly, CloudFormation is 
+better. Secondly, NAT and ELB are the only entrance to the project. That is the best practice for network security that can mitigate the effects 
+of public cyberattacks. Thirdly, IAM roles are used at all kinds of important scenarios, for example, deployment, database visiting, various services visiting.
+
+The source code of entire demo was maintained on Github. The repository URL is https://github.com/A2Inc/A2. There are various languages in it including 
+CSS, Vue, Java, JavaScript, Python, Tex. The contributions of team on this demo are shown on Github as Fig.~\ref{fig3}.
+
+\begin{figure}[htbp]
+    \centerline{\includegraphics[width=260pt]{images/github.png}}
+    \caption{Overview of Github}
+    \label{fig3}
+\end{figure}
+
+Java, Python and Vue are the most useful tool in this demo. The reason of choosing Java is that almost all of the team members has been good at it. Python 
+has a lot of library processing images, so it is the best choice for geospatial imagery. Vue has powerful frontend capabilities, so it is the best for a 
+visualisation demo. Latex are used to generate the report and slides.
 
@@
 \subsection{Data processing}
+The pictures in S3 are based on two essential formats, which is STAC and COG. The satellites generate them everyday. World Bank organized the global night lights project 
+to store these files in S3. When it comes to deal with the satellite imagery, Python has a lot of easy libraries for geospatial calculating. GDAL is the most useful one. 
+It is integrated with Python very well, and is very good at reading and writing raster or vector geospatial file formats.
+
+Two Lambda functions are used for processing them. The first one is to analyse the STAC protocol files. Boundary box can be found from a STAC file, so it is easy to index
+all the imagery together by it and then to find the specific area by it. Root STAC file is the first file we processing, which has all of the child links as json files. 
+Following the child links, there are the list itmes including the COG file URL. COG file is commonly too large to open directly. GDAL can open it easily and calculate radiance 
+value in the file. In the second Lambda function, messages attached COG URL information exchanged by SQS service from the first Lambda function. Because of the complexity 
+of GDAL computation, the second Lambda function is slower than the first one.
+
+The second Lambda function is the main logic of the data processing. First of all, choosing cities or areas is a deep issue. The original design was to show the every administrative 
+cities. But the global administrative cities geospatial data is very difficult to get. Even though Global Administrative Unit Layers (GAUL) data is provided by Food and 
+Agriculture Organization of the United Nation (FAO) \cite{GlobalAd98:online}, the format of these files still needed to research more. So the research areas were reduced 
+to three specific areas, such as east of China, Middle East and New Zealand. Secondly, these three areas are defined in advance because they represent the areas of developed, 
+developing and war. The radiance of these areas would show very different patterns. And reducing areas can help the function processing more quickly. Thirdly, calculating the 
+radiance for every COG file is the core computation. There are intersection areas between the COG file and these three research places. And every pixel in the COG file stores 
+a radiance value for this geospatial point. In the World Bank document, there are some special definitions about the value details, such as -999.3 means no-data value, -1.5 
+means the beginning of the data range \cite{WorldBan13:online}. The value less than 3 could be disruption value. So all of the numbers which are more than 3 could be the 
+sutiable value. At the end, all of the processed information is stored in RDS service. They are date, boundary box, radiance, pixels and so on.
+
+When it comes to the RDS, it is neccessary to introduce the master and slave configuration. Because this global night lights data is stored at us-east-1 region and team members 
+use ap-southeast-1 region, master database is installed at us-east-1 region which is closed to S3 data, and slave database is at another region. The cross-region RDS is 
+provisioned by CloudFormation because there is a ready template. It has to be mentioned that the cross-region cost is not cheap as other services.
 
@@
 
-\subsection{Networking}
+\subsection{Network}
 

### 2021-09-06 Java/src/main/java/com/light/controllers/GithubLogController.java

@@ -129,7 +129,7 @@ public class GithubLogController {
     public ResponseEntity<Map<String,Object>> token(String code, String state, Model model, HttpServletRequest req, HttpSession session) throws Exception {
         Map<String,Object> map = new HashMap<>();
         if (! StringUtils.isNotBlank(code) ||  !StringUtils.isNotBlank(state)) {
-            map.put("r", "no token");
+            map.put("r", "no code");
             return new ResponseEntity<Map<String,Object>>(map,HttpStatus.NON_AUTHORITATIVE_INFORMATION);
         }
         HttpsUtil http = new HttpsUtil();

### 2021-09-08 paper/main.tex

@@
 \subsection{Spring-boot}
-this is the explanation
+Spring-boot is a Java web framework that can help developer build their web instance very quickly. It is easy to build a 
+stand-alone, production-grade application by it \cite{SpringBo66:online}. Because of its features such as no code generation 
+and no requirement for XML configuration, it is the best choose for a Java development team.
 
@@
 
-Two Lambda functions are used for processing them. The first one is to analyse the STAC protocol files. Boundary box can be found from a STAC file, so it is easy to index
+\begin{figure}[htbp]
+    \centerline{\includegraphics[width=260pt]{images/dataprocess.png}}
+    \caption{Data processing}
+    \label{fig4}
+\end{figure}
+
+Two Lambda functions are used for processing them, shown as Fig.~\ref{fig4}. The first one is to analyse the STAC protocol files. Boundary box can be found from a STAC file, so it is easy to index
 all the imagery together by it and then to find the specific area by it. Root STAC file is the first file we processing, which has all of the child links as json files. 
@@
 \subsection{Project management}
+Project management is also a big chanllenge in this special period. Scrum development method was chosen from the first day because two of members
+had already experienced this method. This iterative approach towards the completion of a project can lead the team to the success.
+
+It is important that some tools let the team work like a native team. All of the team members are from China, but nobody knew each other before. 
+So at the first day, the IM platform named Lark, which was widely used in the work place in China, was chosen by team members. Java is the first 
+language in the team because team members are almost good at it. By Github, all of the codes can be easily shared with members and easily taken 
+control of its version. Remote cooperation is not a easy thing, so team members create a event for vedio meeting everyday. At the same time, it 
+is also the agile standup meeting everyday. With the development and research process, some members have to stop to learn more things about the 
+lack of relative knowledge. For example, none of members are good at some key technologies, such as geospatial imagery processing, Vue, AWS usage. 
+So the development plan was always disrupted because of the learning. Thanks to the agile method, the development is not influenced too much by 
+these disruptions.
+
+Because the members were not sharing the true space in a meeting room, the development atmosphere was a little bit strange. It is difficult to know 
+every member's status, so the enthusiasm of development is of critical importance. Somebody went about their tasks with little enthusiasm, and the 
+result would be bad at that aspect. At that time, the role of scrum master was very useful, it ensure the entire development schedule.
 
 \section{Security Considerations}
+Secruity is the important thing in the development. Although some services can enhance the security, but they are usually very expensive, for example, 
+NAT can islote the safer network. There are a lot of details contributing to the security together.
+
+\subsection{IAM}
 
@@
 
-\subsection{User}
-
-\subsection{IAM}
+\subsection{Customer}
 

### 2021-09-08 Frontend/src/router/index.js
1.try world map, 2.write paper

@@ -6,6 +6,7 @@ import Redirect from '@/components/Redirect'
 import TestD3 from '@/components/TestD3'
 import MultiLineChart from '@/components/MultiLineChart'
 import TestEmptyPage from '@/components/TestEmptyPage'
+import WorldMap from '@/components/WorldMap'
 
 Vue.use(Router)
 
@@ -44,6 +45,11 @@ export default new Router({
             path: '/test/empty',
             name: 'TestEmptyPage',
             component: TestEmptyPage
+        },
+        {
+            path: '/test/world',
+            name: 'WorldMap',
+            component: WorldMap
         }
     ]
 })
